%----------------------------------------------------------------------------------------
%	SECTION 2: Preliminaries
%----------------------------------------------------------------------------------------

\section{Preliminaries}



{\begingroup


% Categories & Functors
\newcommand{\QCoh}{\operatorname{QCoh}}
\newcommand{\Coh}{\operatorname{Coh}}
\newcommand{\Ind}{\operatorname{Ind}}
\newcommand{\Fun}{\operatorname{Fun}}
\newcommand{\Map}{\operatorname{Map}} % Mapping space
\newcommand{\End}{\operatorname{End}}
\newcommand{\Mod}{\operatorname{Mod}}
\newcommand{\Alg}{\operatorname{Alg}}
\newcommand{\CAlg}{\operatorname{CAlg}}
\newcommand{\Sp}{\operatorname{Sp}} % Spectra
\newcommand{\PSh}{\mathcal{P}}      % Presheaves

% Geometry
\newcommand{\Spec}{\operatorname{Spec}}
\newcommand{\Sch}{\operatorname{Sch}}
\newcommand{\St}{\operatorname{St}} 
\newcommand{\co}{\mathcal{O}} % Structure sheaf

% Limits and Colimits
\newcommand{\limit}{\varprojlim}
\newcommand{\colimit}{\varinjlim}
\newcommand{\tensor}{\otimes}

% Logic & Sets
\newcommand{\infcat}{$\infty$-category}
\newcommand{\infcats}{$\infty$-categories}
\newcommand{\sSet}{\operatorname{Set}_{\Delta}} % Simplicial Sets

\newcommand{\Cat}{\operatorname{Cat}}            % 经典 1-范畴构成的范畴
\newcommand{\CatI}{\mathcal{C}\mathrm{at}_{\infty}} % 无穷范畴构成的无穷范畴
\newcommand{\Kan}{\mathbf{Kan}}                  % Kan 复形全子范畴
\newcommand{\Ob}{\mathrm{Ob}}  

\newcommand{\C}{\mathcal{C}}
\newcommand{\Sfin}{\mathcal{S}}
\newcommand{\Nerve}{N}
\newcommand{\Rig}{\mathfrak{C}}
\newcommand{\Pinf}{\mathcal{P}}
\newcommand{\Psimp}{\mathcal{P}_{\Delta}}
\subsection{$\infty$-categories}


\begin{definition}[$\infty$-Category]
A simplicial set $K$ is an \textbf{$\infty$-category} if for every $n > 1$ and every \textbf{inner} index $0 < i < n$, every map of simplicial sets $f_0: \Lambda^n_i \to K$ admits an extension to an $n$-simplex $f: \Delta^n \to K$.
\[
\begin{tikzcd}
\Lambda^n_i \arrow[d, hook] \arrow[r, "f_0"] & K \\
\Delta^n \arrow[ru, dashed, "f"'] & 
\end{tikzcd}
\]
\end{definition}

\begin{definition}[Simplicial Category]
A \textbf{simplicial category} (or $\sSet$-enriched category) $\mathcal{C}$ is a category where:
\begin{enumerate}
    \item For any two objects $X, Y \in \mathcal{C}$, the collection of morphisms between them is not a set, but a \textbf{simplicial set} $\Map_{\mathcal{C}}(X, Y)$.
    \item For any three objects $X, Y, Z \in \mathcal{C}$, the composition map 
    \[ \Map_{\mathcal{C}}(Y, Z) \times \Map_{\mathcal{C}}(X, Y) \to \Map_{\mathcal{C}}(X, Z) \]
    is a morphism of simplicial sets and satisfies the usual associativity and identity axioms.
\end{enumerate}
A simplicial category $\mathcal{C}$ is \textbf{locally Kan} if for every pair of objects $X, Y \in \Ob(\mathcal{C})$, the mapping simplicial set $\Map_{\mathcal{C}}(X, Y)$ is a Kan complex.
\end{definition}




\begin{definition}[Simplicial Nerve $N_{\Delta}$]
The \textbf{simplicial nerve} $N_{\Delta}(\mathcal{C})$ is the simplicial set defined by the assignment:
\[ 
    N_{\Delta}(\mathcal{C})_n = \mathrm{Hom}_{\Cat_{\Delta}}(\mathfrak{C}[\Delta^n], \mathcal{C}) 
\]
where $\mathfrak{C}[\Delta^n]$ is the \textbf{rigidification} of the $n$-simplex $\Delta^n$ into a simplicial category.
\end{definition}

\begin{definition}[$\infty$-category via $N_\Delta$]
An \textbf{$\infty$-category} (or quasicategory) is a simplicial set $K$ that is equivalent to the simplicial nerve of some locally Kan simplicial category $\mathcal{C}$.
\[ K \simeq N_{\Delta}(\mathcal{C}) \]
\end{definition}





\begin{theorem}[Joyal-Lurie]
There exists a Quillen equivalence between the Joyal model structure on $\sSet$ (modeling quasicategories) and the Bergner model structure on $\Cat_{\Delta}$ (modeling simplicial categories):
\[
\mathfrak{C}[\cdot] : \sSet \rightleftarrows \Cat_{\Delta} : N_{\Delta}.
\]
Specifically, for any simplicial category $\mathcal{C}$ where mapping spaces are Kan complexes, its simplicial nerve $N_{\Delta}(\mathcal{C})$ is a quasicategory.
\end{theorem}




\begin{definition}[Free Cocompletion]
Let $\mathcal{C}$ be a small \infcat{}. An \infcat{} $\PSh(\mathcal{C})$ is called the \textbf{free cocompletion} of $\mathcal{C}$ if it satisfies the following universal property:

\begin{enumerate}
    \item $\PSh(\mathcal{C})$ admits all small colimits.
    \item There exists a functor $j: \mathcal{C} \to \PSh(\mathcal{C})$ (called the Yoneda embedding) such that for any \infcat{} $\mathcal{D}$ which admits small colimits, composition with $j$ induces an equivalence of \infcats{}:
    \[
        \Fun^L(\PSh(\mathcal{C}), \mathcal{D}) \xrightarrow{\sim} \Fun(\mathcal{C}, \mathcal{D}).
    \]
\end{enumerate}
Here, $\Fun^L$ denotes the full subcategory of functors that preserve small colimits (left adjoints).
\end{definition}


\begin{definition}[The \infcat{} of Spaces]
Let $\mathcal{S}$ denote the \infcat{} of spaces. It is defined in two equivalent ways:

\begin{enumerate}
    \item \textbf{Via Dwyer-Kan Localization:} \\
    Let $W$ be the class of weak homotopy equivalences in $\sSet$. We define $\mathcal{S}$ as the homotopy coherent nerve of the simplicial localization:
    \[
        \mathcal{S} \coloneqq N\bigl(\sSet[W^{-1}]\bigr).
    \]
    Equivalently, via Kan complexes: $\mathcal{S} \simeq N(\Kan)$.

    \item \textbf{Via Free Cocompletion:} \\
    The \infcat{} $\mathcal{S}$ is the free cocompletion of the point $*$. That is, it is the category of presheaves:
    \[
        \mathcal{S} \simeq \PSh(*).
    \]
    Universal Property: For any cocomplete \infcat{} $\mathcal{C}$, there is an equivalence $\Fun^L(\mathcal{S}, \mathcal{C}) \simeq \mathcal{C}$.
\end{enumerate}
\end{definition}

\begin{theorem}
Let $K$ be an $\infty$-category (quasi-category). Let $\C = \Rig[K]$ be its associated simplicial category (via rigidification). The construction of the presheaf $\infty$-category commutes with the nerve construction in the following sense:

\begin{enumerate}
    \item \textbf{Simplicial Side:} Consider the category of simplicial presheaves $\Psimp(\C) := \mathrm{Fun}_{\Delta}(\C^{op}, \Sfin_{\text{Kan}})$. This category admits a simplicial model structure (projective structure).
    
    \item \textbf{Infinity Side:} Consider the $\infty$-category of presheaves $\Pinf(K) := \mathrm{Fun}(K^{op}, \Sfin)$.
    
    \item \textbf{Equivalence:} There is an equivalence of $\infty$-categories:
    \[ \Pinf(K) \simeq \Nerve \left( \Psimp(\C)^{\mathrm{cf}} \right) \]
    where $\Psimp(\C)^{\mathrm{cf}}$ denotes the full simplicial subcategory of fibrant-cofibrant objects in the model category of simplicial presheaves.
\end{enumerate}
In summary, the presheaf of an $\infty$-category is modeled by the nerve of the strictly cocomplete simplicial category of enriched presheaves.
\end{theorem}

\begin{remark}[Homotopy Category via Fibrant-Cofibrant Objects]
To correctly construct the homotopy category $\mathrm{Ho}(\mathcal{M})$ from a simplicial model category $\mathcal{M}$, one cannot simply take the path components $\pi_0$ of the mapping spaces between arbitrary objects. 

Instead, one must restrict attention to the full subcategory of \textbf{fibrant-cofibrant objects}, denoted $\mathcal{M}_{cf}$. It is only within this subcategory that the simplicial mapping spaces $\mathrm{Map}_{\mathcal{M}}(X, Y)$ are guaranteed to be Kan complexes representing the correct derived mapping spaces. The morphisms in the homotopy category are thus given by:
\[
[X, Y]_{\mathrm{Ho}(\mathcal{M})} \cong \pi_0 \mathrm{Map}_{\mathcal{M}}(X, Y) \quad \text{for } X, Y \in \mathcal{M}_{cf}.
\]
For general objects $X, Y$, one must first replace them with weakly equivalent fibrant-cofibrant objects (via cofibrant replacement $QX$ and fibrant replacement $RY$) to compute this group.
\end{remark}
\endgroup}

{\begingroup
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\Map}{\mathrm{Map}}
\newcommand{\Sp}{\text{Sp}}
\newcommand{\Exc}{\text{Exc}}
\newcommand{\Sfin}{\mathcal{S}_*^{\text{fin}}}
\newcommand{\uMap}{\underline{\mathrm{Map}}}
\newcommand{\Sone}{\mathbb{S}}
\newcommand{\Vlim}{\varprojlim}
\newcommand{\Clim}{\varinjlim}
\newcommand{\Ssphere}{\mathbb{S}}
\newcommand{\wedgeS}{\wedge}
\newcommand{\Stab}{\mathrm{Stab}} % 稳定化算子
\newcommand{\Sspace}{\mathcal{S}} % 空间范畴
\newcommand{\otimesD}{\otimes_{\mathcal{D}}}
\newcommand{\Unit}{\mathbf{1}_{\mathcal{D}}}

\newcommand{\SigInf}{\Sigma^\infty}    % Suspension Spectrum Functor
\newcommand{\OmeInf}{\Omega^\infty}    % Infinite Loop Space Functor


\subsection{Stable $\infty$-Category}

\begin{definition}[Loop Object]
For any object $X \in \C$, the loop object $\Omega X$ is the limit of the diagram $0 \to X \leftarrow 0$. It fits into the following pullback square:
\[
\begin{tikzcd}
\Omega X \arrow[r] \arrow[d] \arrow[dr, phantom, "\lrcorner", very near start] & 0 \arrow[d] \\
0 \arrow[r] & X
\end{tikzcd}
\]
Intuitively, $\Omega X \simeq 0 \times_X 0$.
\end{definition}

\begin{definition}[Suspension Object]
For any object $X \in \C$, the suspension object $\Sigma X$ is the colimit of the diagram $0 \leftarrow X \to 0$. It fits into the following pushout square:
\[
\begin{tikzcd}
X \arrow[r] \arrow[d] \arrow[dr, phantom, "\ulcorner", very near end] & 0 \arrow[d] \\
0 \arrow[r] & \Sigma X
\end{tikzcd}
§\]
Intuitively, $\Sigma X \simeq 0 \amalg_X 0$.
\end{definition}
\begin{definition}[Stable $\infty$-Category]
An $\infty$-category $\C$ is called \textbf{stable} if it satisfies the following conditions:
\begin{enumerate}
    \item There exists a zero object $0 \in \C$ (i.e., $\C$ is pointed).
    \item Every morphism in $\C$ admits a kernel and a cokernel.
    \item A triangle in $\C$ is a pushout square if and only if it is a pullback square.
\end{enumerate}
\end{definition}
\begin{definition}[The Stabilization of an $\infty$-Category]
Let $\mathcal{C}$ be an $\infty$-category admitting finite limits. The process of constructing the stable $\infty$-category associated to $\mathcal{C}$ proceeds in two stages:

\begin{enumerate}
    \item \textbf{Pointed View (Formation of $\mathcal{C}_*$):} \\
    First, we construct the \textit{pointed} $\infty$-category $\mathcal{C}_*$. Assuming $\mathcal{C}$ has a terminal object $*$, $\mathcal{C}_*$ is defined as the under-category of the terminal object:
    \[
    \mathcal{C}_* := \mathcal{C}_{*/} \cong \text{Fun}(\Delta^1, \mathcal{C}) \times_{\text{Fun}(\{0\}, \mathcal{C})} \{*\}
    \]
    Objects in $\mathcal{C}_*$ are morphisms $* \to X$ in $\mathcal{C}$ (i.e., objects equipped with a base point). In $\mathcal{C}_*$, the object corresponding to the identity $* \to *$ serves as a \textit{zero object} (both initial and terminal). Consequently, the loop functor $\Omega: \mathcal{C}_* \to \mathcal{C}_*$ is well-defined by $\Omega X = * \times_X *$.

    \item \textbf{Stabilization (Formation of $\text{Sp}(\mathcal{C})$):} \\
    The \textit{stabilization} of $\mathcal{C}$, denoted as $\text{Sp}(\mathcal{C})$ (or $\text{Stab}(\mathcal{C})$), is defined as the $\infty$-category of spectrum objects in $\mathcal{C}_*$. It is constructed as the homotopy limit of the tower of loop functors:
    \[
    \text{Sp}(\mathcal{C}) := \varprojlim \left( \cdots \xrightarrow{\Omega} \mathcal{C}_* \xrightarrow{\Omega} \mathcal{C}_* \xrightarrow{\Omega} \mathcal{C}_* \right)
    \]
    Explicitly, an object $E \in \text{Sp}(\mathcal{C})$ consists of a sequence $\{E_n\}_{n \geq 0}$ of objects in $\mathcal{C}_*$ together with equivalences $E_n \xrightarrow{\sim} \Omega E_{n+1}$ for each $n$. This construction forces the suspension functor $\Sigma$ to be an equivalence, rendering $\text{Sp}(\mathcal{C})$ a stable $\infty$-category.
\end{enumerate}
\end{definition}

\begin{theorem}[Universal Property of Stabilization]
Let $\C$ be an $\infty$-category with finite limits and a terminal object $\ast$. Let $\C_* = \C_{\ast/}$ be its pointed version. The stabilization $\Sp(\C)$ is characterized by the following equivalent descriptions:

\begin{enumerate}
    \item \textbf{Internal Construction (Loop Towers):} 
    $\Sp(\C)$ is the homotopy limit of the sequence of loop functors:
    \[
    \Sp(\C) \simeq \varprojlim \left( \cdots \xrightarrow{\Omega} \C_* \xrightarrow{\Omega} \C_* \xrightarrow{\Omega} \C_* \right)
    \]
    An object in $\Sp(\C)$ is an $\Omega$-spectrum, i.e., a sequence $\{E_n\}_{n \geq 0}$ in $\C_*$ with equivalences $E_n \simeq \Omega E_{n+1}$.

    \item \textbf{External Construction (Excision):} 
    $\Sp(\C)$ is equivalent to the $\infty$-category of pointed excisive functors from the category of finite pointed spaces $\Sfin$ to $\C$:
    \[
    \Sp(\C) \simeq \Exc_*(\Sfin, \C)
    \]
    A functor $F: \Sfin \to \C$ belongs to $\Exc_*(\Sfin, \C)$ if $F(\ast) \simeq \ast$ and $F$ maps every pushout square in $\Sfin$ to a pullback square in $\C$.
\end{enumerate}

Furthermore, the stabilization $\Sp(\C)$ is the universal stable $\infty$-category under $\C$: for any stable $\infty$-category $\mathcal{D}$, the functor $\Sp(\C) \to \mathcal{D}$ induces an equivalence of $\infty$-categories $\text{Fun}^{\text{lex}}(\Sp(\C), \mathcal{D}) \simeq \text{Fun}^{\text{lex}}(\C, \mathcal{D})$, where $\text{Fun}^{\text{lex}}$ denotes the $\infty$-category of left exact functors.
\end{theorem}

\begin{remark}[Distinction between $\Stab(\C)$ and $\Sp$]
It is essential to distinguish between the abstract process of stabilization and the specific category of spectra:
\begin{enumerate}
    \item \textbf{The Category of Spectra ($\Sp$):} Historically and by convention, $\Sp$ refers specifically to the stabilization of the $\infty$-category of pointed spaces $\Sspace_{\ast}$. That is:
    \[ \Sp \simeq \Stab(\Sspace) \simeq \varprojlim (\dots \xrightarrow{\Omega} \Sspace_{\ast} \xrightarrow{\Omega} \Sspace_{\ast}) \]
    This category serves as the unit object in the $\infty$-category of stable $\infty$-categories and provides the ground for stable homotopy theory.

    \item \textbf{Stabilization of an Arbitrary $\infty$-Category ($\Stab(\C)$):} For any $\infty$-category $\C$ with finite limits, $\Stab(\C)$ is the stable $\infty$-category constructed as the limit of the tower of loop functors:
    \[ \Stab(\C) = \varprojlim (\dots \xrightarrow{\Omega} \C_{\ast} \xrightarrow{\Omega} \C_{\ast}) \]
    While $\Stab(\C)$ is always a stable $\infty$-category, it may not possess a symmetric monoidal structure (like the smash product) unless $\C$ itself is equipped with a compatible monoidal structure.

    \item \textbf{The Relation:} Any stable $\infty$-category $\mathcal{D}$ is naturally tensored over $\Sp$. In this sense, $\Sp$ plays a role analogous to the ring of integers $\mathbb{Z}$ in abelian groups: for any $D \in \mathcal{D}$ and $E \in \Sp$, there is a well-defined object $E \otimes D \in \mathcal{D}$.
\end{enumerate}
\end{remark}

\begin{definition}[Internal Mapping Spectrum in $\Stab(\C)$]
Let $\C$ be a \textbf{closed symmetric monoidal $\infty$-category} $(\C, \otimes, \mathbf{1})$ that admits finite limits. Assume further that the tensor product $\otimes$ is compatible with the stabilization (i.e., it preserves colimits in each variable). 

Let $\mathcal{D} = \Stab(\C)$ be the resulting stable $\infty$-category, equipped with the induced symmetric monoidal structure $\otimesD$. For any objects $X, Y \in \mathcal{D}$, the \textbf{internal mapping spectrum} is defined as the object $\uMap_{\mathcal{D}}(X, Y) \in \mathcal{D}$ that satisfies the following conditions:

\begin{enumerate}
    \item \textbf{Adjunction Property:} It is the right adjoint to the tensor product functor. For any object $Z \in \mathcal{D}$, there is a natural equivalence of mapping spaces:
    \[ \Map_{\mathcal{D}}(Z \otimesD X, Y) \simeq \Map_{\mathcal{D}}(Z, \uMap_{\mathcal{D}}(X, Y)) \]
    
    \item \textbf{Spectrum Level Structure:} In terms of the sequence of objects $\{E_n\} \in \C_{\ast}$ representing the spectrum, the $n$-th level of the internal mapping spectrum is given by:
    \[ \uMap_{\mathcal{D}}(X, Y)_n \simeq \uMap_{\C}(X, \Sigma^n Y) \]
    where $\uMap_{\C}$ denotes the internal Hom in the underlying category $\C$ (if it exists) or the corresponding enrichment.
\end{enumerate}
\end{definition}

\begin{definition}[Mapping Spectrum]
Let $X$ and $Y$ be spectra in $\Sp$. The \textbf{mapping spectrum} from $X$ to $Y$, denoted as $\uMap(X, Y) \in \Sp$, is the unique spectrum (up to equivalence) characterized by the following properties:

\begin{enumerate}
    \item \textbf{Adjunction (Internal Hom):}
    For any spectrum $Z$, there is a natural equivalence of mapping spaces:
    \[
    \Map_{\Sp}(Z \wedgeS X, Y) \simeq \Map_{\Sp}(Z, \uMap(X, Y))
    \]
    This identifies $\uMap(X, Y)$ as the right adjoint to the smash product functor $( - \wedgeS X )$.

    \item \textbf{Omega-Spectrum Structure:}
    The $n$-th space of the mapping spectrum is equivalent to the space of maps from $X$ to the $n$-th suspension of $Y$:
    \[
    \uMap(X, Y)_n \simeq \Map_{\Sp}(X, \Sigma^n Y)
    \]
    The structure maps $\Sigma \uMap(X, Y)_n \to \uMap(X, Y)_{n+1}$ are induced by the stability of $\Sp$.
\end{enumerate}
\end{definition}


\begin{definition}[Homotopy Groups in $\Stab(\C)$]
Let $\C$ be a closed symmetric monoidal $\infty$-category with finite limits, and let $\D = \Stab(\C)$ be its stabilization with unit object $\Unit$. 
\begin{enumerate}
    \item \textbf{Homotopy Groups of an Object:} For any object $E \in \D$ and $n \in \mathbb{Z}$, the $n$-th homotopy group of $E$ is defined as the abelian group of homotopy classes of maps from the $n$-shifted unit object:
    \[ \pi_n(E) := [\Sigma^n \Unit, E]_{\D}  \]
    
    \item \textbf{Homotopy Groups of the Mapping Spectrum:} Let $\uMap_{\D}(X, Y) \in \D$ be the internal mapping spectrum between $X, Y \in \D$. Its homotopy groups characterize the graded morphisms between the two objects:
    \[ \pi_n \uMap_{\D}(X, Y) \cong [X, \Sigma^n Y]_{\D} \cong [\Sigma^{-n} X, Y]_{\D} \]
    where $[-, -]_{\D}$ denotes the set of homotopy classes i.e. the $0$-th homotopy group of the kan complex $\Map_{\D}(-, -)$.
\end{enumerate}
\end{definition}

\begin{remark}
The distinction lies in the target category:
\begin{itemize}
    \item $\Map_{\D}(X, Y) \in \mathcal{S}$ is a \textbf{space} (Kan complex). It represents the mapping space in the $\infty$-categorical sense.
    \item $\uMap_{\D}(X, Y) \in \D$ is a \textbf{spectrum} (Internal Hom). It is an object of the stable category $\D$ that stabilizes the mapping space.
\end{itemize}
In terms of homotopy groups: $\pi_n \Map_{\D}(X, Y) \cong \pi_n \uMap_{\D}(X, Y)$ for $n \ge 0$, because every spectrum is $\Omega$-spectrum in $\Stab(\C)$.
\end{remark}

\begin{construction}[Stabilization of a Suspension Spectrum]
Let $X \in \Sspace_{\ast}$ be a pointed space (or generally an object in a pointed $\infty$-category $\mathcal{C}$ with finite colimits). The construction of its associated \textbf{suspension spectrum} $\SigInf X \in \Sp$ proceeds as follows:

\begin{enumerate}
    \item \textbf{The Prespectrum Construction:}
    First, we form a \textit{prespectrum} $P_X$ by iterating the suspension functor $\Sigma$ on $X$. This is given by the sequence of spaces:
    \[ (P_X)_n := \Sigma^n X, \quad \text{for } n \ge 0 \]
    together with the structural maps (identities):
    \[ \sigma_n: \Sigma((P_X)_n) = \Sigma(\Sigma^n X) \xrightarrow{id} \Sigma^{n+1} X = (P_X)_{n+1} \]

    \item \textbf{Spectrification (The L-functor):}
    Since $P_X$ is not necessarily an $\Omega$-spectrum (i.e., the adjoint maps $(P_X)_n \to \Omega (P_X)_{n+1}$ are not equivalences), we apply the \textit{spectrification functor} $L$ (or stabilization) to convert it into a true spectrum. The resulting object is the suspension spectrum:
    \[ \SigInf X := L(P_X) \]
    Conceptually, the $k$-th space of this stable object is the colimit:
    \[ (\SigInf X)_k \simeq \operatorname*{colim}_{m \to \infty} \Omega^m \Sigma^{m+k} X \]

    \item \textbf{Universal Property (Adjunction):}
    The construction defines the left adjoint functor $\SigInf$ in the stabilization adjunction:
    \[
    \begin{tikzcd}
        \Sspace_{\ast}\arrow[r, "\SigInf", bend left] & \Sp \arrow[l, "\OmeInf", bend left]
    \end{tikzcd}
    \]
    where for any spectrum $E$, the right adjoint is given by $\OmeInf E := E_0$ (the 0-th space of the $\Omega$-spectrum $E$).
\end{enumerate}
\end{construction}

\begin{remark}[Bousfield-Friedlander Structure and Stabilization]
    The Bousfield-Friedlander model structure $\mathcal{M}_{\mathrm{BF}}$ on the category of prespectra is the left Bousfield localization of the strict model structure $\mathcal{M}_{\mathrm{strict}}$. The three classes of morphisms in $\mathcal{M}_{\mathrm{BF}}$ are characterized as follows:
    \begin{itemize}
        \item \textbf{Cofibrations:} These are exactly the same as the strict cofibrations (levelwise inclusions that satisfy the appropriate cell complex conditions).
        \item \textbf{Weak Equivalences:} These are the \textit{stable weak equivalences}, i.e., maps $f: X \to Y$ that induce isomorphisms on stable homotopy groups $\pi_n^{S}(X) \cong \pi_n^{S}(Y)$ for all $n \in \mathbb{Z}$.
        \item \textbf{Fibrations:} These are the maps that satisfy the right lifting property with respect to acyclic cofibrations. Specifically, a map $p: E \to B$ is a BF-fibration if it is a levelwise fibration and the square 
        \[
        \begin{tikzcd}
            E_n \arrow[r] \arrow[d, "p_n"] & \Omega E_{n+1} \arrow[d, "\Omega p_{n+1}"] \\
            B_n \arrow[r] & \Omega B_{n+1}
        \end{tikzcd}
        \]
        is a homotopy pullback for all $n$.
    \end{itemize}
    
    The transition from $\mathcal{M}_{\mathrm{strict}}$ to $\mathcal{M}_{\mathrm{BF}}$ captures the essence of stabilization. Since the fibrant objects in this structure are exactly the $\Omega$-spectra, the \textbf{fibrant replacement} of a prespectrum $X$ in $\mathcal{M}_{\mathrm{BF}}$ is precisely its \textbf{stabilization} (spectrification). 
    
    If $R_{\mathrm{BF}}$ denotes the fibrant replacement functor, we have a natural stable equivalence $j: X \xrightarrow{\sim} R_{\mathrm{BF}}(X)$, where $R_{\mathrm{BF}}(X)$ is an $\Omega$-spectrum. In the stable homotopy category, this is equivalent to the classical stabilization $QX = \Omega^\infty \Sigma^\infty X$:
    \[
    \begin{tikzcd}
        X \arrow[r, "j", "\sim_{\text{stable}}"'] \arrow[d, equal] & R_{\mathrm{BF}}(X) \arrow[d, "\simeq"] \\
        X \arrow[r, "\text{Stabilization}"] & QX
    \end{tikzcd}
    \]
    Thus, the Bousfield-Friedlander model structure provides the formal homotopy-theoretic machinery where "becoming an $\Omega$-spectrum" is equivalent to "becoming fibrant."
\end{remark}

\begin{definition}
The \textbf{homotopy category functor} $ho$ is the change-of-base functor induced by the path-components functor $\pi_0: \mathbf{sSet} \to \mathbf{Set}$. For a category $\mathcal{C}$ enriched over simplicial sets, $ho(\mathcal{C})$ is the $\mathbf{Set}$-enriched category with the same objects as $\mathcal{C}$ and morphism sets defined by:
\[ \text{Hom}_{ho(\mathcal{C})}(X, Y) = \pi_0(\text{Map}_{\mathcal{C}}(X, Y)) \]
Composition in $ho(\mathcal{C})$ is inherited from the enriched composition in $\mathcal{C}$ via the product-preserving property of $\pi_0$.
\end{definition}

\begin{proposition}
Let $\mathcal{C}$ be a locally Kan simplicial category. Let $N_{\Delta}$ denote the homotopy coherent nerve and $N$ denote the classical nerve. There is a natural isomorphism of simplicial sets (or categories):
\[ ho(N_{\Delta}(\mathcal{C})) \cong N(ho(\mathcal{C})) \]
\end{proposition}

\begin{example}[The Stable Homotopy Category]
Let $\mathcal{S}p$ be the stable $\infty$-category of spectra. The classical \textbf{stable homotopy category} $\mathsf{SHC}$ is precisely its homotopy category:
\[ \mathsf{SHC} \cong ho(\mathcal{S}p) \]
Under the $ho$ functor, the enriched mapping spaces $\text{Map}_{\mathcal{S}p}(X, Y)$ are replaced by their sets of path-components $\pi_0$. The stable property of $\mathcal{S}p$ (the equivalence of fiber and cofiber sequences) ensures that $ho(\mathcal{S}p)$ inherits the structure of a \textbf{triangulated category}.
\end{example}


\endgroup}

\begingroup 

\subsection{$\infty$-Operad }

\begin{definition}[$\infty$-Operator Category]
An \textbf{$\infty$-operator category} is an $\infty$-category $\mathcal{B}$ equipped with a specified subcategory of \textit{inert morphisms} $\mathcal{B}^{\mathrm{inert}}$, satisfying the following two structural axioms illustrated by commutative diagrams:

\begin{enumerate}
    \item \textbf{Active-Inert Factorization:} 
    There exists a class of \textit{active morphisms} such that every morphism $f: X \to Z$ in $\mathcal{B}$ factors essentially uniquely as an active morphism followed by an inert morphism.
    \[
    \begin{tikzcd}
        X \arrow[rr, "f"] \arrow[dr, "f^{\mathrm{act}} \text{ (Mix)}"'] & & Z \\
         & Y \arrow[ur, "f^{\mathrm{inert}} \text{ (Select)}"'] &
    \end{tikzcd}
    \]
    Here, $f^{\mathrm{act}}$ performs the operations (combining inputs), and $f^{\mathrm{inert}}$ performs the structural projection.

    \item \textbf{Elementary Decomposition:} 
    There exists a set of \textit{elementary objects} (or colors) $\{U_\alpha\}$. Every object $X \in \mathcal{B}$ is determined by its inert projections to these elementary objects. Specifically, the collection of inert morphisms $\{\rho^i\}$ exhibits $X$ as a product:
    \[
    \begin{tikzcd}[column sep=small]
        & X \arrow[dl, "\rho^1"'] \arrow[d, "\rho^2"] \arrow[dr, "\rho^n"] & \\
        U_{i_1} & U_{i_2} & U_{i_n}
    \end{tikzcd}
    \]
    This implies an equivalence $X \simeq U_{i_1} \times U_{i_2} \times \dots \times U_{i_n}$, ensuring that complex objects are merely aggregates of elementary slots.
\end{enumerate}
\end{definition}

\begin{definition}[$\infty$-Operator Category]
An \textbf{$\infty$-operator category} is an $\infty$-category $\mathcal{B}$ equipped with a specified factorization structure, consisting of two subcategories: \textit{active morphisms} ($\mathcal{B}^{\mathrm{act}}$) and \textit{inert morphisms} ($\mathcal{B}^{\mathrm{inert}}$). These satisfy the following two axioms:

\begin{enumerate}
    \item \textbf{Active-Inert Factorization System:} 
    The pair $(\mathcal{B}^{\mathrm{act}}, \mathcal{B}^{\mathrm{inert}})$ forms an \textit{orthogonal factorization system} on $\mathcal{B}$. 
    
    This means that every morphism $f: X \to Z$ in $\mathcal{B}$ factors essentially uniquely as an active morphism followed by an inert morphism:
    \[
    \begin{tikzcd}[column sep=large, row sep=large]
        X \arrow[rr, "f"] \arrow[dr, "f^{\mathrm{act}} "'] & & Z \\
         & Y \arrow[ur, "f^{\mathrm{inert}}"'] &
    \end{tikzcd}
    \]
    Here, the intermediate object $Y$ and the active map $f^{\mathrm{act}}$ are not arbitrary; they are \textbf{determined} by the image of $f$ under this factorization system. 

    \item \textbf{Elementary Decomposition (Segal Core):} 
    There exists a set of elementary objects $\mathcal{E} \subset \mathrm{Ob}(\mathcal{B})$. For any object $X \in \mathcal{B}$, let $\Lambda_X$ be the set of all inert morphisms targeting $\mathcal{E}$:
    \[
        \Lambda_X := \{ \rho: X \to U \mid \rho \in \mathcal{B}^{\mathrm{inert}}, U \in \mathcal{E} \}
    \]
    We require that the canonical map induced by these morphisms is an equivalence:
    \[
        X \xrightarrow{\quad \simeq \quad} \prod_{\rho \in \Lambda_X} \mathrm{codom}(\rho)
    \]
\end{enumerate}

\end{definition}


\begin{definition}[$\mathcal{B}$-Operad]
Let $\mathcal{B}$ be an $\infty$-operator category. 
A \textbf{$\mathcal{B}$-operad} is a map of simplicial sets $p: \mathcal{C}^\otimes \to \mathcal{B}$ satisfying the following three conditions:

\begin{enumerate}
    \item \textbf{Inner Fibration:} The map $p$ is an inner fibration of simplicial sets. That is, for every $0 < k < n$, $p$ has the right lifting property with respect to the inner horn inclusion $\Lambda^n_k \hookrightarrow \Delta^n$.
    
    \item \textbf{Inert Lifting Property:} For every inert morphism $f: X \to Y$ in $\mathcal{B}$ and every object $C \in \mathcal{C}^\otimes$ such that $p(C) = X$, there exists a $p$-coCartesian edge $\bar{f}: C \to C'$ in $\mathcal{C}^\otimes$ such that $p(\bar{f}) = f$.
    
    \item \textbf{Segal Condition:} For every object $X \in \mathcal{B}$, let $\{X \xrightarrow{f_i} U_i\}_{i \in I}$ be the collection of inert morphisms decomposing $X$ into elementary objects (as dictated by the structure of $\mathcal{B}$). The functor induced by the $p$-coCartesian lifts of these inert morphisms,
    \[
        \mathcal{C}^\otimes_X \xrightarrow{\quad \simeq \quad} \prod_{i \in I} \mathcal{C}^\otimes_{U_i},
    \]
    is an equivalence of $\infty$-categories.
\end{enumerate}
\end{definition}

\begin{definition}[$\mathcal{O}$-Algebra Object]
Let $\mathcal{B}$ be an $\infty$-operator category. Let $p: \mathcal{O}^\otimes \to \mathcal{B}$ and $q: \mathcal{C}^\otimes \to \mathcal{B}$ be \textbf{$\mathcal{B}$-operad}.
An \textbf{$\mathcal{O}$-algebra object in $\mathcal{C}$} is a map of $\infty$-operads over $\mathcal{B}$. Explicitly, it is a functor
\[
A: \mathcal{O}^\otimes \longrightarrow \mathcal{C}^\otimes
\]
satisfying two conditions:

\begin{enumerate}
    \item \textbf{Commutativity over Base (Compatibility):} 
    The functor $A$ respects the projection to the base category $\mathcal{B}$. The following diagram commutes:
    \[
    \begin{tikzcd}[row sep=large, column sep=small]
        \mathcal{O}^\otimes \arrow[rr, "A"] \arrow[dr, "p"'] & & \mathcal{C}^\otimes \arrow[dl, "q"] \\
         & \mathcal{B} &
    \end{tikzcd}
    \]
    (i.e., $q \circ A = p$).

    \item \textbf{Inert Preservation (The Operad Map Condition):} 
    The functor $A$ carries inert morphisms to inert morphisms.
    
    Specifically, if $f$ is an \textit{inert morphism} in $\mathcal{O}^\otimes$ (meaning $f$ is a $p$-coCartesian lift of an inert map in $\mathcal{B}$), then its image $A(f)$ must be an \textit{inert morphism} in $\mathcal{C}^\otimes$ (meaning $A(f)$ is a $q$-coCartesian lift of that same map in $\mathcal{B}$).
\end{enumerate}

The $\infty$-category of all such algebras is denoted by $\mathrm{Alg}_{\mathcal{O}}(\mathcal{C})$.

\end{definition}

\begin{example}[\textbf{The Zoo of Operads and Their Bases}]
We classify common algebraic structures by specifying the underlying \textbf{Base Category} $\mathcal{B}$ (which dictates the geometry of inputs) and the \textbf{Operad} $\mathcal{O}^\otimes$ (which dictates the operations) as a fibration $p: \mathcal{O}^\otimes \to \mathcal{B}$.

\begin{enumerate}
    \item \textbf{The Commutative Case ($E_\infty$)}
    \begin{itemize}
        \item \textbf{Base:} $\mathcal{B} = N(\mathrm{Fin}_*)$ (Symmetric/Unordered inputs).
        \item \textbf{Operad:} $\mathcal{O}^\otimes = \mathrm{Comm}^\otimes := N(\mathrm{Fin}_*)$.
        \item \textbf{Structure Map:} The identity map $\mathrm{id}: N(\mathrm{Fin}_*) \to N(\mathrm{Fin}_*)$.
        \item \textbf{Resulting Algebra:} \textbf{Commutative $\infty$-Algebra}.
        \item \textbf{Note:} Since the map is the identity, the fiber over any operation is a point. There is essentially only one way to combine inputs (order doesn't matter).
    \end{itemize}

    \item \textbf{The Associative Case ($A_\infty$)}
    \begin{itemize}
        \item \textbf{Base:} $\mathcal{B} = N(\mathrm{Fin}_*)$.
        \item \textbf{Operad:} $\mathcal{O}^\otimes = \mathrm{Ass}^\otimes$ (The Associative Operad).
        \item \textbf{Structure Map:} The "forgetful" functor that forgets the linear ordering of the fibers.
        \item \textbf{Resulting Algebra:} \textbf{Associative $\infty$-Algebra}.
        \item \textbf{Note:} The fiber over $\langle n \rangle \to \langle 1 \rangle$ is equivalent to the symmetric group $\Sigma_n$. This allows inputs to be permuted (by the base), but the operation distinguishes the order of multiplication ($x_1 x_2 \neq x_2 x_1$).
    \end{itemize}

    \item \textbf{The Little $k$-Disks Case ($E_k$)}
    \begin{itemize}
        \item \textbf{Base:} $\mathcal{B} = N(\mathrm{Fin}_*)$.
        \item \textbf{Operad:} $\mathcal{O}^\otimes = \mathbb{E}_k^\otimes$.
        \item \textbf{Structure Map:} The projection from the space of disk embeddings.
        \item \textbf{Resulting Algebra:} \textbf{$E_k$-Algebra}.
        \item \textbf{Note:} Interpolates between Associative ($k=1$) and Commutative ($k=\infty$).
    \end{itemize}

    \item \textbf{The Lie Case ($L_\infty$)}
    \begin{itemize}
        \item \textbf{Base:} $\mathcal{B} = N(\mathrm{Fin}_*)$.
        \item \textbf{Operad:} $\mathcal{O}^\otimes = \mathrm{Lie}^\otimes$.
        \item \textbf{Resulting Algebra:} \textbf{$L_\infty$-Algebra} (Homotopy Lie Algebra).
        \item \textbf{Note:} Typically considered over a stable target category (like chain complexes).
    \end{itemize}

    \item \textbf{The Non-Symmetric / Planar Case}
    \begin{itemize}
        \item \textbf{Base:} $\mathcal{B} = N(\Delta)^{op}$ (The Simplex Category; Linear/Ordered inputs).
        \item \textbf{Operad:} $\mathcal{O}^\otimes = N(\Delta)^{op}$.
        \item \textbf{Structure Map:} The identity map.
        \item \textbf{Resulting Algebra:} \textbf{Associative Monoid} (in the strict sense).
        \item \textbf{Note:} Here, the base category itself forbids permutation. There is no symmetric group action to even consider.
    \end{itemize}
\end{enumerate}


\end{example}

\begin{definition}[Endomorphism $\infty$-Category]
Let $\mathcal{C}$ be an $\infty$-category. The \textbf{Endomorphism $\infty$-Category}, denoted by $\text{End}(\mathcal{C})$, is defined as the functor $\infty$-category $\text{Fun}(\mathcal{C}, \mathcal{C})$. 

It forms a \textbf{monoidal $\infty$-category} where the monoidal structure is determined by the composition of endofunctors:
\begin{enumerate}
    \item The tensor product is given by composition: $F \otimes G := F \circ G$.
    \item The unit object is given by the identity functor: $\mathbb{I} := \text{Id}_{\mathcal{C}}$.
\end{enumerate}
\end{definition}



\begin{definition}[Spaces of Monads and Comonads]
Let $\mathcal{C}$ be an $\infty$-category, and let $\text{End}(\mathcal{C})$ denote the monoidal $\infty$-category of endofunctors on $\mathcal{C}$ (equipped with the composition product).
The $\infty$-categories (or spaces) of Monads and Comonads as the categories of associative algebra objects in $\text{End}(\mathcal{C})$ and its opposite, respectively:

\begin{enumerate}
    \item The \textbf{$\infty$-category of Monads} is defined as:
    \[
    \text{Mnd}(\mathcal{C}) := \text{Alg}_{\mathcal{A}ss}(\text{End}(\mathcal{C}))
    \]
    
    \item The \textbf{$\infty$-category of Comonads} is defined as:
    \[
    \text{CoMnd}(\mathcal{C}) := \text{Alg}_{\mathcal{A}ss}(\text{End}(\mathcal{C})^{op})
    \]
\end{enumerate}
The objects of $\text{Mnd}(\mathcal{C})$ are referred to as \textbf{Monads} on $\mathcal{C}$, and the objects of $\text{CoMnd}(\mathcal{C})$ are referred to as \textbf{Comonads} on $\mathcal{C}$.
\end{definition}

\begin{definition}[Reedy Category]
A small category $\mathcal{R}$ is a \textbf{Reedy category} if it is equipped with a degree function $d: \text{Ob}(\mathcal{R}) \to \lambda$ (where $\lambda$ is an ordinal) and two subcategories $\overrightarrow{\mathcal{R}}$ (the direct category) and $\overleftarrow{\mathcal{R}}$ (the inverse category), such that:
\begin{enumerate}
    \item Every non-identity morphism in $\overrightarrow{\mathcal{R}}$ raises the degree.
    \item Every non-identity morphism in $\overleftarrow{\mathcal{R}}$ lowers the degree.
    \item Every morphism $f$ in $\mathcal{R}$ factors uniquely as $f = g \circ h$, where $h \in \overleftarrow{\mathcal{R}}$ and $g \in \overrightarrow{\mathcal{R}}$.
\end{enumerate}
\end{definition}

\begin{definition}[The Reedy Model Structure]
Let $\mathcal{M}$ be a model category and $\mathcal{R}$ be a Reedy category. The category of diagrams $\text{Fun}(\mathcal{R}, \mathcal{M})$ is equipped with the \textbf{Reedy model structure}, where a morphism $f: X \to Y$ is defined to be:

\begin{enumerate}
    \item A \textbf{Weak Equivalence} if it is a levelwise weak equivalence. That is, for every object $\alpha \in \mathcal{R}$, the map $f_\alpha: X_\alpha \to Y_\alpha$ is a weak equivalence in $\mathcal{M}$.

    \item A \textbf{Cofibration} if for every $\alpha \in \mathcal{R}$, the \textbf{relative latching map} $\lambda_\alpha(f)$ is a cofibration in $\mathcal{M}$.
    Here, $\lambda_\alpha(f)$ is the map induced by the pushout of the latching objects:
    \[
    \lambda_\alpha(f): X_\alpha \amalg_{L_\alpha X} L_\alpha Y \longrightarrow Y_\alpha
    \]
    where the \textit{latching object} is defined as $L_\alpha X = \text{colim}_{\partial \vec{\mathcal{R}}/\alpha} X$.

    \item A \textbf{Fibration} if for every $\alpha \in \mathcal{R}$, the \textbf{relative matching map} $\mu_\alpha(f)$ is a fibration in $\mathcal{M}$.
    Here, $\mu_\alpha(f)$ is the map induced into the pullback of the matching objects:
    \[
    \mu_\alpha(f): X_\alpha \longrightarrow M_\alpha X \times_{M_\alpha Y} Y_\alpha
    \]
    where the \textit{matching object} is defined as $M_\alpha X = \lim_{\alpha / \partial \overleftarrow{\mathcal{R}}} X$.
\end{enumerate}
\end{definition}

\begin{proposition}[Latching and Matching as Monadic Structures]
Let $\mathcal{R}$ be a Reedy category. For any degree $\alpha$, consider the truncation inclusion of the category of degrees strictly lower than $\alpha$:
\[ u: \mathcal{R}_{< \alpha} \hookrightarrow \mathcal{R}_{\le \alpha} \]
Let $u^*$ be the restriction functor. We identify the Latching and Matching objects via the adjunctions defining the skeleton and coskeleton:

\begin{enumerate}
    \item \textbf{Latching as a Monad (Skeleton):}
    The pair $u_! \dashv u^*$ generates a \textbf{Monad} $T = u_! \circ u^*$ (Left Kan Extension followed by restriction). The Latching object is the value of this monad:
    \[
    L_\alpha X \cong (T(X))_\alpha = (\text{Lan}_u (u^* X))_\alpha
    \]
    The canonical map $L_\alpha X \to X_\alpha$ corresponds to the monad algebra structure map (or the counit of the adjunction).

    \item \textbf{Matching as a Comonad (Coskeleton):}
    The pair $u^* \dashv u_*$ generates a \textbf{Comonad} $G = u_* \circ u^*$ (Right Kan Extension followed by restriction). The Matching object is the value of this comonad:
    \[
    M_\alpha X \cong (G(X))_\alpha = (\text{Ran}_u (u^* X))_\alpha
    \]
    The canonical map $X_\alpha \to M_\alpha X$ corresponds to the comonad coalgebra structure map (or the unit of the adjunction).
\end{enumerate}

\end{proposition}

\begin{definition}[Monadic and Comonadic Resolution]
Let $\mathcal{C}$ be a category and $X$ an object in $\mathcal{C}$. We define the canonical resolutions generated by monads and comonads as follows:

\begin{enumerate}
    \item \textbf{Monadic Resolution:}
    Let $(T, \mu, \eta)$ be a \textbf{Monad} on $\mathcal{C}$. The \textbf{Bar Construction} provides an augmented simplicial object $B_\bullet(X)$ resolving $X$:
    \[
    \begin{tikzcd}
    \dots \arrow[r, shift left] \arrow[r, shift right] 
    & T^3 X \arrow[r, shift left] \arrow[r] \arrow[r, shift right] 
    & T^2 X \arrow[r, shift left] \arrow[r, shift right] 
    & TX \arrow[r, "\epsilon"] 
    & X
    \end{tikzcd}
    \]
    The face maps $d_i$ are given by the multiplication $\mu$, and degeneracy maps $s_i$ by the unit $\eta$. This construction typically serves as a \textbf{cofibrant replacement} of $X$.

    \vspace{1em}

    \item \textbf{Comonadic Resolution:}
    Let $(G, \delta, \epsilon)$ be a \textbf{Comonad} on $\mathcal{C}$. The \textbf{Cobar Construction} provides an augmented cosimplicial object $C^\bullet(X)$ resolving $X$:
    \[
    \begin{tikzcd}
    X \arrow[r, "\eta"] 
    & GX \arrow[r, shift left] \arrow[r, shift right] 
    & G^2 X \arrow[r, shift left] \arrow[r] \arrow[r, shift right] 
    & G^3 X \arrow[r, shift left] \arrow[r, shift right] 
    & \dots
    \end{tikzcd}
    \]
    The coface maps $d^i$ are given by the comultiplication $\delta$, and codegeneracy maps $s^i$ by the counit $\epsilon$. This construction typically serves as a \textbf{fibrant replacement} of $X$.
\end{enumerate}

\end{definition}


\begin{example}[\textbf{Reedy Latching and Matching}]
In a Reedy category $\mathcal{R}$, resolutions arise from Kan extensions along the filtration $u: \mathcal{R}_{< \alpha} \hookrightarrow \mathcal{R}_{\le \alpha}$.
\begin{itemize}
    \item \textbf{Latching (Monad):} The Latching object $L_\alpha X$ is generated by the \textbf{Skeleton Monad} $T = u_! u^*$ (Left Kan extension followed by restriction).
    \[ L_\alpha X \cong (T X)_\alpha \]
    \item \textbf{Matching (Comonad):} The Matching object $M_\alpha X$ is generated by the \textbf{Coskeleton Comonad} $G = u_* u^*$ (Right Kan extension followed by restriction).
    \[ M_\alpha X \cong (G X)_\alpha \]
\end{itemize}
\end{example}

\begin{example}[\textbf{The Cotangent Complex (André-Quillen)}]
Used to define the derived cotangent complex $\mathbb{L}_{A/k}$.
\begin{itemize}
    \item \textbf{Monad:} The \textbf{Free Algebra Monad} $T$ on the category of $k$-modules (or sets).
    \[ T(V) = \text{Sym}_k(V) \quad (\text{Polynomial Algebra}) \]
    \item \textbf{Resolution:} The simplicial resolution $P_\bullet \to A$ is the Bar construction $B_\bullet(T, T, A)$. The cotangent complex is derived from applying differentials $\Omega^1_{P_\bullet/k} \otimes_{P_\bullet} A$.
\end{itemize}
\end{example}

\begin{example}[\textbf{The Postnikov Tower}]
Decomposing a space $X$ into its homotopy types.
\begin{itemize}
    \item \textbf{Monad:} The \textbf{$n$-Truncation Monad} $\tau_{\le n}$ (or $P_n$).
    \[ T_n(X) = \tau_{\le n}(X) \]
    This is an \textit{idempotent} monad (localization). The tower is the limit sequence $\dots \to T_n X \to T_{n-1} X$.
    \item \textit{Note:} Dually, the \textbf{Whitehead Tower} uses the $n$-connected cover Comonad $\tau_{>n}$.
\end{itemize}
\end{example}

\begin{example}[\textbf{Projective and Injective Resolution}]
Let $R$ be a ring and $M$ an $R$-module.

\begin{enumerate}
    \item \textbf{Projective Resolution (The Bar Construction):}
    Using the free-forgetful adjunction $F \dashv U$, we define the \textbf{Free Monad} $T = F \circ U$. Since $T(M)$ is a free module, the associated Bar construction yields a canonical projective resolution:
    \[
    \dots \longrightarrow T^3 M \longrightarrow T^2 M \longrightarrow T M \xrightarrow{\epsilon} M \longrightarrow 0
    \]
    The boundary maps are alternating sums of the monad multiplication $\mu: T^2 \to T$.

    \item \textbf{Injective Resolution (The Cobar Construction):}
    Using the forgetful-cofree adjunction $U \dashv C$ (where $C(A) = \text{Hom}_{\mathbb{Z}}(R, A)$), we define the \textbf{Cofree Comonad} $G = C \circ U$. Since $G(M)$ is an injective module, the associated Cobar construction yields a canonical injective resolution:
    \[
    0 \longrightarrow M \xrightarrow{\eta} G M \longrightarrow G^2 M \longrightarrow G^3 M \longrightarrow \dots
    \]
    The boundary maps are alternating sums of the comonad comultiplication $\delta: G \to G^2$.
\end{enumerate}

\end{example}

\begin{example}[\textbf{The Spectrification Monad on Prespectra}]
Let $\mathcal{P}$ be the category of Prespectra (sequences of spaces with maps $\Sigma E_n \to E_{n+1}$). The process of converting a naive suspension spectrum into a genuine $\Omega$-spectrum is governed by the \textbf{Spectrification Monad} $\mathbb{L}$.

\begin{enumerate}
    \item \textbf{The Level-wise Monad:}
    We define a Monad $\mathbb{L}: \mathcal{P} \to \mathcal{P}$ by applying the spatial stabilization monad $Q = \Omega^\infty \Sigma^\infty$ to \textit{each level} of the spectrum independently:
    \[ (\mathbb{L} E)_n := Q(E_n) = \mathop{\text{colim}}_{k} \Omega^k \Sigma^k E_n \]
    
    \item \textbf{Application to Suspension Spectra:}
    If $E = \Sigma^\infty X$ is the suspension spectrum of $X$ (where $E_n = \Sigma^n X$), applying this monad yields:
    \[ (\mathbb{L}(\Sigma^\infty X))_n = Q(\Sigma^n X) \]
    The result $\mathbb{L}(\Sigma^\infty X)$ is an \textbf{$\Omega$-spectrum}. This is the \textit{fibrant replacement} of $\Sigma^\infty X$ in the stable model structure.

    \item \textbf{Distinction from Adams Resolution:}
    \begin{itemize}
        \item The \textbf{Adams/Bousfield-Kan resolution} builds a tower $X \to QX \to Q^2 X \dots$ to resolve the \textit{space} $X$.
        \item The \textbf{Spectrification Monad} $\mathbb{L}$ acts once (essentially as a completion) to fix the \textit{structure} of the spectrum, ensuring the adjoint structure maps $E_n \to \Omega E_{n+1}$ become weak equivalences.
    \end{itemize}
\end{enumerate}

\end{example}

\begin{example}[\textbf{The $R$-Completion of a Space}]
Let $R$ be a commutative ring (typically $\mathbb{Z}_p$ or $\mathbb{Q}$). The Bousfield-Kan resolution constructs the "$R$-completion" of a space $X$, effectively translating algebraic information (homology with coefficients in $R$) into homotopy information.

\begin{enumerate}
    \item \textbf{The Monad ($R$-Linearization):}
    Let $R: \mathcal{S} \to \mathcal{S}$ be the monad that assigns to a simplicial set $K$ the free simplicial $R$-module generated by $K$ (forgetting the module structure back to a simplicial set).
    \[ X \xrightarrow{\eta} R(X) \]
    Intuitively, this replaces every simplex of $X$ with the free $R$-module generated by its vertices.

    \item \textbf{The Cosimplicial Space (Bar Construction):}
    Applying the Monad iteratively generates a \textbf{cosimplicial space} $R^\bullet X$:
    \[
    \begin{tikzcd}
    X \arrow[r, "\eta"] 
    & R(X) \arrow[r, shift left] \arrow[r, shift right] 
    & R(R(X)) \arrow[r, shift left] \arrow[r] \arrow[r, shift right] 
    & R^3(X) \cdots
    \end{tikzcd}
    \]
    This tower resolves $X$ by spaces that are algebraically simple (generalized Eilenberg-MacLane spaces).

    \item \textbf{Totalization ($R$-Completion):}
    The \textbf{Totalization} (Homotopy Limit) of this cosimplicial space defines the $R$-completion of $X$:
    \[ X^\wedge_R := \text{Tot}(R^\bullet X) \simeq \mathop{\text{holim}}_{\Delta} R^\bullet X \]
    
    \item \textbf{The Spectral Sequence:}
    This resolution yields the \textbf{Bousfield-Kan Spectral Sequence}, which computes the homotopy groups of the completion from the cohomology of $X$:
    \[ E_2^{s,t} \cong \text{Ext}^s_{\text{Comod}}(R, H_*(X; R))_t \implies \pi_{t-s}(X^\wedge_R) \]
    For $R=\mathbb{Z}_p$, this computes the homotopy groups of the $p$-adic completion of $X$.
\end{enumerate}

\end{example}
\endgroup


\begingroup
non-trival operator In hom/ 
delet 
push-out = pull-back = linear = stab
 lifting obstruction
Tw(C) 
twisted fiber product 
spectral sequence 
Hochschild+Hodge Realization = /Cyclic Homology/Topological Cyclic Homology
Ladder of Higher Coherence
Bockstein, Transgression/k-invarient,Massey,Toda,Steenrod,Hurewicz,Samelson,Pontryagin,Whitehead,Cup Product,Dyer-Lashof,Adams,Landweber-Novikov,Browder Bracket,Functional Cohomology Operations
Transfer (Becker-Gottlieb Transfer)
Geometric Filtration/Resolution Filtration/Coefficient Filtration corr sps
Exact Couple/Filtered Complex
The Rees Construction/Deformation
non-trival operation = correlation of rees algebra
Deformation Quantization
The Dennis Trace:cat C to K(C) to Hochschild
Lurie:K-theory is Universal invarient of additivity, tr is factor through
bisimplicial

\subsection{Obstructions and Traces}


\begin{definition}[$p$-Cartesian Morphism]
Let $p: \mathcal{E} \to \mathcal{B}$ be a functor. A morphism $\phi: v \to u$ in $\mathcal{E}$ is called \textbf{$p$-Cartesian} if it satisfies the following universal property:

For every object $w \in \mathcal{E}$ and every morphism $\psi: w \to u$, given a morphism $g: p(w) \to p(v)$ in $\mathcal{B}$ such that $p(\psi) = p(\phi) \circ g$, there exists a \textbf{unique} morphism $\tilde{g}: w \to v$ in $\mathcal{E}$ such that $p(\tilde{g}) = g$ and $\phi \circ \tilde{g} = \psi$.

This relationship is depicted in the following commutative diagram, where the vertical arrows represent the projection $p$, and the dashed arrow represents the unique lift:
\[
\begin{tikzcd}[row sep=2.5em, column sep=2.5em]
% Top layer (Category E)
w \arrow[rr, "\psi"] \arrow[dr, dashed, "\exists ! \tilde{g}"] \arrow[dd, "p" description, gray] 
& & u \arrow[dd, "p" description, gray] \\
& v \arrow[ur, "\phi"'] \arrow[dd, "p" description, gray] & \\
% Bottom layer (Category B)
p(w) \arrow[rr, "p(\psi)" near end] \arrow[dr, "g"'] 
& & p(u) \\
& p(v) \arrow[ur, "p(\phi)"'] & 
\end{tikzcd}
\]
\end{definition}



\begin{definition}[Grothendieck Fibration]
A functor $p: \mathcal{E} \to \mathcal{B}$ is a \textbf{Grothendieck fibration} if, for every object $u$ in $\mathcal{E}$ and every morphism $f: X \to p(u)$ in $\mathcal{B}$, there exists a morphism $\phi: v \to u$ in $\mathcal{E}$ satisfying the following conditions:
\begin{itemize}
    \item \textbf{Lifting:} $p(\phi) = f$;
    \item \textbf{Universality:} $\phi$ is a $p$-Cartesian morphism.
\end{itemize}
This existence of a Cartesian lift is depicted by the diagram:
\[
\begin{tikzcd}[row sep=2.5em, column sep=2.5em]
v \arrow[r, "\exists \phi", dashed] \arrow[d, "p"'] & u \arrow[d, "p"] \\
X \arrow[r, "f"] & p(u)
\end{tikzcd}
\]
\end{definition}

\begin{definition}[Grothendieck Construction]
Let $\mathcal{C}$ be a category and $F: \mathcal{C}^{op} \to \mathbf{Cat}$ be a contravariant functor (an indexed category). The \textbf{Grothendieck construction} of $F$, denoted by $\int F$ (or $\mathcal{C}_F$), is the category defined as follows:

\begin{itemize}
    \item \textbf{Objects:} Pairs $(c, x)$, where $c$ is an object of $\mathcal{C}$ and $x$ is an object of the category $F(c)$.
    
    \item \textbf{Morphisms:} A morphism from $(c, x)$ to $(d, y)$ is a pair $(u, \alpha)$, where:
    \begin{itemize}
        \item $u: c \to d$ is a morphism in $\mathcal{C}$;
        \item $\alpha: x \to F(u)(y)$ is a morphism in the fiber category $F(c)$.
    \end{itemize}
    Note that since $F$ is contravariant, $F(u)$ is a functor $F(d) \to F(c)$, so $F(u)(y)$ lies in $F(c)$.

    \item \textbf{Composition:} Given morphisms $(u, \alpha): (c, x) \to (d, y)$ and $(v, \beta): (d, y) \to (e, z)$, the composite is defined by:
    \[
    (v, \beta) \circ (u, \alpha) = (v \circ u, \; F(u)(\beta) \circ \alpha)
    \]
    Here, $F(u)(\beta)$ maps $F(u)(y)$ to $F(u)(F(v)(z)) = F(v \circ u)(z)$.
\end{itemize}
There is a canonical projection functor $p: \int F \to \mathcal{C}$ given by $p(c, x) = c$ and $p(u, \alpha) = u$. This functor $p$ makes $\int F$ a \textbf{Grothendieck fibration} over $\mathcal{C}$, with the fiber over $c$ isomorphic to $F(c)$.
\end{definition}

\begin{definition}[Left and Right Fibrations]
Let $p: X \to S$ be a morphism of simplicial sets. The map $p$ is classified based on the \textit{right lifting property} against horn inclusions $\Lambda^n_k \hookrightarrow \Delta^n$ as follows:

\begin{enumerate}
    \item $p$ is called a \textbf{left fibration} if it has the right lifting property for all $0 \le k < n$.
    \item $p$ is called a \textbf{right fibration} if it has the right lifting property for all $0 < k \le n$.
\end{enumerate}

In either case, the condition asserts that for the specified range of $k$ and any $n \ge 1$, given any commutative square
\[
\begin{tikzcd}[row sep=large, column sep=large]
\Lambda^n_k \arrow[r] \arrow[d, hook] & X \arrow[d, "p"] \\
\Delta^n \arrow[r] \arrow[ur, dashed, "\exists"] & S
\end{tikzcd}
\]
there exists a lift $\Delta^n \to X$ making the diagram commute.

Intuitively, left fibrations model covariant functors (transporting fibers forward along paths starting at $k=0$), while right fibrations model contravariant functors (transporting fibers backward along paths ending at $k=n$).
\end{definition}

\begin{remark}[Directionality of Lifting]
The distinction between left and right fibrations generalizes the classical categorical notions of \textbf{pushforward} and \textbf{pullback}. The choice of the horn inclusion $\Lambda^1_k \hookrightarrow \Delta^1$ determines the flow of information relative to a morphism $u: x \to y$ in the base:

\begin{enumerate}
    \item \textbf{Right Fibration ($\Lambda^1_1$): Pullback / Cartesian.}
    The horn $\Lambda^1_1$ fixes the \textit{target} ($y$) and the morphism $u$. Lifting implies existence of a domain over $x$.
    \[
    \begin{tikzcd}[row sep=tiny]
     \cdot \arrow[r, dashed, "\text{lift}"] & \bullet \\
     x \arrow[r, "u"'] & y
    \end{tikzcd}
    \quad \implies \quad
    \text{Information flows } y \to x \quad (\text{Contravariant } u^*)
    \]

    \item \textbf{Left Fibration ($\Lambda^1_0$): Pushforward / Co-Cartesian.}
    The horn $\Lambda^1_0$ fixes the \textit{source} ($x$) and the morphism $u$. Lifting implies existence of a codomain over $y$.
    \[
    \begin{tikzcd}[row sep=tiny]
     \bullet \arrow[r, dashed, "\text{lift}"] & \cdot \\
     x \arrow[r, "u"'] & y
    \end{tikzcd}
    \quad \implies \quad
    \text{Information flows } x \to y \quad (\text{Covariant } u_!)
    \]
\end{enumerate}
\end{remark}
\begin{definition}[Twisted Arrow $\infty$-Category]
Let $\mathcal{C}$ be an $\infty$-category. The \textbf{twisted arrow category} $\text{Tw}(\mathcal{C})$ is defined as the \textbf{Grothendieck construction} (or unstraightening) of the mapping space functor.

Explicitly, let $\chi$ be the functor classifying the mapping spaces:
\[
\begin{aligned}
\chi: (\mathcal{C} \times \mathcal{C}^{op})^{op} &\longrightarrow \mathcal{S} \\
(X, Y) &\longmapsto \text{Map}_{\mathcal{C}}(X, Y).
\end{aligned}
\]
Then $\text{Tw}(\mathcal{C}) \simeq \int \chi$. Consequently, $\text{Tw}(\mathcal{C})$ is characterized as the total space of the \textbf{right fibration}
\[
p: \text{Tw}(\mathcal{C}) \longrightarrow \mathcal{C} \times \mathcal{C}^{op}
\]
associated to $\chi$. Combinatorially, this is modeled by the simplicial set whose $n$-simplices are maps $\Delta^n \star (\Delta^n)^{op} \to \mathcal{C}$. 

\[
\text{Hom}_{\mathbf{sSet}}(\Delta^n, \text{Tw}(\mathcal{C})) \cong \text{Hom}_{\mathbf{sSet}}\big((\Delta^n)^{op} \star \Delta^n, \mathcal{C}\big),
\]

For any pair of objects $(x, y)$, the fiber of $p$ is the mapping space:
\[
\begin{tikzcd}[row sep=large, column sep=large]
\text{Map}_{\mathcal{C}}(x, y) \arrow[r, hook] \arrow[d] & \text{Tw}(\mathcal{C}) \arrow[d, "p", "\text{Right Fib}"'] \\
\{(y, x)\} \arrow[r, hook] & \mathcal{C} \times \mathcal{C}^{op}
\end{tikzcd}
\]
\end{definition}

\begin{remark}[Local Systems on $\text{Tw}(\mathcal{C})$ and Coends]
A \textbf{local system} on the twisted arrow category is a functor $\mathcal{F}: \text{Tw}(\mathcal{C}) \to \mathcal{D}$ (where $\mathcal{D}$ is a target $\infty$-category like $\mathcal{S}$ or $\textbf{Spectra}$).

The significance of such a system lies in its role in computing \textbf{Coends} and \textbf{Traces}.
Let $M: \mathcal{C}^{op} \times \mathcal{C} \to \mathcal{D}$ be a bimodule (a functor of two variables). We can pull $M$ back along the canonical projection $p: \text{Tw}(\mathcal{C}) \to \mathcal{C} \times \mathcal{C}^{op}$ to obtain a local system $p^*M$ on $\text{Tw}(\mathcal{C})$. 

The value of this local system on an object $(f: A \to B) \in \text{Tw}(\mathcal{C})$ is simply $M(A, B)$. The \textbf{Coend} of the bimodule $M$ is then geometrically realized as the colimit of this local system over the twisted arrow category:
\[
\int^{c \in \mathcal{C}} M(c, c) \simeq \operatorname*{colim}_{(f: A \to B) \in \text{Tw}(\mathcal{C})} M(A, B).
\]
Intuitively, $\text{Tw}(\mathcal{C})$ provides the necessary "morphisms between morphisms" to glue the diagonal terms $M(c, c)$ together, creating a global invariant (the Trace) of the category.
\end{remark}

\begin{remark}[The Geometric Hierarchy of $\text{Tw}(\mathcal{C})$]
In the $\infty$-categorical setting, the twisted arrow category $\text{Tw}(\mathcal{C})$ shifts the geometric dimension of objects in $\mathcal{C}$ by one level. We can visualize the $k$-morphisms of $\text{Tw}(\mathcal{C})$ as $(k+1)$-dimensional shapes in $\mathcal{C}$:

\vspace{1em}

\noindent\textbf{1. Objects (The Lines)} \\
An object in $\text{Tw}(\mathcal{C})$ corresponds to a 1-simplex (an arrow) in $\mathcal{C}$.
\[
\begin{tikzcd}
    A \arrow[r, "f", thick] & B
\end{tikzcd}
\]

\vspace{1em}
\hrule
\vspace{1em}

\noindent\textbf{2. 1-Morphisms (The Twisted Squares)} \\
A morphism $\phi: f \to g$ represents a factorization $f \simeq v \circ g \circ u$. Geometrically, this is a square filled by a homotopy $\sigma$.
\[
\begin{tikzcd}[row sep=large, column sep=large]
    A \arrow[r, "u"] \arrow[d, "f"'] & A' \arrow[d, "g"] \\
    B \arrow[ur, phantom, "\sigma", "\simeq" description] & B' \arrow[l, "v"]
\end{tikzcd}
\]

\vspace{1em}
\hrule
\vspace{1em}

\noindent\textbf{3. 2-Morphisms (The Homotopy Tunnels)} \\
A 2-morphism represents a coherence between two factorizations. If we have a "blue" factorization $\phi=(u,v)$ and a "red" factorization $\phi'=(u',v')$, a 2-morphism is the \textbf{deformation} (tunnel) connecting them.

In the diagram below, the vertical objects $f$ and $g$ form the fixed pillars, while the factorization maps flow from the front (blue) to the back (red) via the violet homotopies:

\begin{center}
\begin{tikzpicture}[scale=1.2, >=Stealth] 
    %% 1. DEFINE NODES FIRST (To avoid "No shape named" errors) %%
    
    % Nodes for BACK Face (Target: u', v')
    \node (Ab) at (2.2, 2.2) {$A$};
    \node (Apb) at (5.2, 2.2) {$A'$};
    \node (Bb) at (2.2, -0.8) {$B$};
    \node (Bpb) at (5.2, -0.8) {$B'$};

    % Nodes for FRONT Face (Source: u, v)
    \node (A) at (0, 0) {$A$};
    \node (Ap) at (3, 0) {$A'$};
    \node (B) at (0, -3) {$B$};
    \node (Bp) at (3, -3) {$B'$};

    %% 2. DRAW FILLS (Visual cues) %%
    \fill[red, opacity=0.05] (2.2, 2.2) -- (5.2, 2.2) -- (5.2, -0.8) -- (2.2, -0.8) -- cycle;
    \fill[blue, opacity=0.05] (0, 0) -- (3, 0) -- (3, -3) -- (0, -3) -- cycle;

    %% 3. DRAW BACK LAYER ARROWS %%
    \draw[->, red, thick] (Ab) -- (Apb) node[midway, above] {$u'$};
    \draw[->, red, thick] (Bpb) -- (Bb) node[midway, below] {$v'$};
    % Dashed fixed pillars (Back)
    \draw[->, dashed] (Ab) -- (Bb) node[midway, left, font=\scriptsize] {$f$};
    \draw[->, dashed] (Apb) -- (Bpb) node[midway, right, font=\scriptsize] {$g$};

    %% 4. DRAW CONNECTIONS (Now safe because nodes exist) %%
    \draw[gray, dotted] (A) -- (Ab);
    \draw[gray, dotted] (Ap) -- (Apb);
    \draw[gray, dotted] (B) -- (Bb);
    \draw[gray, dotted] (Bp) -- (Bpb);

    %% 5. DRAW FRONT LAYER ARROWS %%
    \draw[->, blue, thick] (A) -- (Ap) node[midway, above, fill=white, inner sep=0.5pt] {$u$};
    \draw[->, blue, thick] (Bp) -- (B) node[midway, below, fill=white, inner sep=0.5pt] {$v$};
    % Solid fixed pillars (Front)
    \draw[->, thick] (A) -- (B) node[midway, left] {$f$};
    \draw[->, thick] (Ap) -- (Bp) node[midway, right] {$g$};

    %% 6. DRAW HOMOTOPIES (Violet Arrows) %%
    % From u (front) to u' (back)
    \draw[->, violet, shorten >=10pt, shorten <=10pt] (1.5, 0) -- (3.7, 2.2) 
        node[midway, fill=white, inner sep=1pt, sloped] {\tiny $\alpha: u \Rightarrow u'$};
        
    % From v (front) to v' (back)
    \draw[->, violet, shorten >=10pt, shorten <=10pt] (1.5, -3) -- (3.7, -0.8) 
        node[midway, fill=white, inner sep=1pt, sloped] {\tiny $\beta: v \Rightarrow v'$};
\end{tikzpicture}
\end{center}

This entire solid represents a 3-simplex in $\mathcal{C}$, encoding the data that $f \simeq v \circ g \circ u$ is homotopic to $f \simeq v' \circ g \circ u'$.
\end{remark}
\begin{definition}[Local System on the Twisted Arrow $\infty$-Category]
Let $\mathcal{C}$ be an $\infty$-category and $\mathcal{D}$ be a target $\infty$-category (e.g., the category of spectra $\text{Sp}$).

A \textbf{$\mathcal{D}$-valued local system on $\text{Tw}(\mathcal{C})$} is a functor
\[
\mathcal{L}: \text{Tw}(\mathcal{C}) \longrightarrow \mathcal{D}
\]
satisfying the condition that $\mathcal{L}$ sends every morphism in $\text{Tw}(\mathcal{C})$ to an \textbf{equivalence} in $\mathcal{D}$.

Explicitly, this means:
\begin{enumerate}
    \item \textbf{On Objects:} For every object in $\text{Tw}(\mathcal{C})$, which is a 1-morphism $f: x \to y$ in $\mathcal{C}$, the local system assigns an object:
    \[
    \mathcal{L}(f) \in \text{Obj}(\mathcal{D}).
    \]
    
    \item \textbf{On Morphisms:} For every morphism $\phi: f \to g$ in $\text{Tw}(\mathcal{C})$, which corresponds to a homotopy commutative square in $\mathcal{C}$ (a factorization $f \simeq v \circ g \circ u$):
    \[
    \begin{tikzcd}
        x \arrow[r, "u"] \arrow[d, "f"'] & x' \arrow[d, "g"] \\
        y & y' \arrow[l, "v"]
    \end{tikzcd}
    \]
    the induced map in $\mathcal{D}$ is an equivalence:
    \[
    \mathcal{L}(\phi): \mathcal{L}(f) \xrightarrow{\sim} \mathcal{L}(g).
    \]
\end{enumerate}

Consequently, $\mathcal{L}$ factors through the fundamental $\infty$-groupoid of the twisted arrow category:
\[
\mathcal{L}: \Pi_{\infty}(\text{Tw}(\mathcal{C})) \longrightarrow \mathcal{D}.
\]
\end{definition}

\begin{definition}[Topological Chiral Homology and Cohomology]
Let $\mathcal{C}$ be a spectral $\infty$-category and let $\mathcal{F}: \operatorname{Tw}(\mathcal{C}) \to \operatorname{Sp}$ be a local system on its twisted arrow $\infty$-category (as defined previously).

We define the \textbf{Topological Chiral Homology} (also known as Factorization Homology over $S^1$) of $\mathcal{C}$ with coefficients in $\mathcal{F}$ as the colimit of the local system:
\[
\int_{S^1} \mathcal{F} \quad := \quad \operatorname{colim}_{\operatorname{Tw}(\mathcal{C})} \mathcal{F}.
\]

Dually, we define the \textbf{Topological Chiral Cohomology} of $\mathcal{C}$ with coefficients in $\mathcal{F}$ as the limit of the local system:
\[
\oint^{S^1} \mathcal{F} \quad := \quad \lim_{\operatorname{Tw}(\mathcal{C})} \mathcal{F}.
\]
\end{definition}




\begin{example}[The Ladder of Theories on $\operatorname{Tw}(\mathcal{C})$: Explicit Formulas]
Here we detail the specific formulas for Homology ($\operatorname{colim}$) and Cohomology ($\operatorname{lim}$) at each level of complexity.

\begin{enumerate}
    % ------------------------------------------------
    % LEVEL 1: SINGULAR
    % ------------------------------------------------
    \item \textbf{Level 1: Singular Theory (Topological)} \\
    \textit{Context:} $\mathcal{C}$ is a discrete category (or space $X$).
    \begin{itemize}
        \item \textbf{Local System:} Constant functor $\underline{\mathbb{Z}}$.
        \item \textbf{Homology (Singular Chain Complex):}
        \[
        H_*(B\mathcal{C}; \mathbb{Z}) \cong \operatorname{Tor}_*^{\mathbb{Z}[\mathcal{C}]}(\mathbb{Z}, \mathbb{Z}).
        \]
        \textit{Geometric Formula:} $H_*(X) = \ker \partial / \operatorname{im} \partial$ using the standard singular boundary operator $\partial = \sum (-1)^i d_i$.
        \item \textbf{Cohomology (Singular Cochain Complex):}
        \[
        H^*(B\mathcal{C}; \mathbb{Z}) \cong \operatorname{Ext}^*_{\mathbb{Z}[\mathcal{C}]}(\mathbb{Z}, \mathbb{Z}).
        \]
        \textit{Tw(C) Formula:} $\displaystyle \lim_{\operatorname{Tw}(\mathcal{C})} \underline{\mathbb{Z}}$.
    \end{itemize}

    % ------------------------------------------------
    % LEVEL 2: CLASSICAL HOCHSCHILD
    % ------------------------------------------------
    \item \textbf{Level 2: Classical Hochschild / Baues-Wirsching (Linear)} \\
    \textit{Context:} Associative $k$-algebra $A$ (or $k$-linear category). $M$ is an $A$-bimodule.
    \begin{itemize}
        \item \textbf{Local System:} The bimodule $M$ regarded as a functor on $\operatorname{Tw}(A)$.
        \item \textbf{Homology (Bar Construction):}
        \[
        HH_*(A; M) \cong \operatorname{Tor}_*^{A \otimes A^{op}}(A, M).
        \]
        \textit{Explicit Complex:} The homology of the chain complex $(C_*(A, M), b)$:
        \[ C_n = M \otimes A^{\otimes n}, \quad b(m \otimes a_1 \dots) = ma_1 \otimes a_2 \dots + \sum \dots + (-1)^n a_n m \otimes \dots \]
        \item \textbf{Cohomology (Derivations/Extensions):}
        \[
        HH^*(A; M) \cong \operatorname{Ext}^*_{A \otimes A^{op}}(A, M).
        \]
        \textit{Explicit Complex:} The cohomology of $(C^*(A, M), \delta)$, where 1-cocycles are derivations: $\delta f(a, b) = a f(b) - f(ab) + f(a)b$.
    \end{itemize}

    % ------------------------------------------------
    % LEVEL 3: TOPOLOGICAL HOCHSCHILD (THH/THC)
    % ------------------------------------------------
    \item \textbf{Level 3: Topological Hochschild (Spectral)} \\
    \textit{Context:} Ring spectrum $A$ (an $S$-algebra).
    \begin{itemize}
        \item \textbf{Local System:} The algebra $A$ itself (as a spectral bimodule).
        \item \textbf{Homology (Derived Tensor Product):}
        \[
        \operatorname{THH}(A) \simeq A \wedge_{A \wedge A^{op}} A \quad (\text{Symmetric Monoidal Product}).
        \]
        \textit{Geometric Formula:} The geometric realization of the cyclic nerve $|N^{cyc}_\bullet(A)|$.
        \item \textbf{Cohomology (Topological Center):}
        \[
        \operatorname{THC}(A) \simeq F_{A \wedge A^{op}}(A, A) \simeq \operatorname{RHom}_{A \wedge A^{op}}(A, A).
        \]
        This computes the \textbf{Derived Center} of the ring spectrum $A$.
    \end{itemize}

    % ------------------------------------------------
    % LEVEL 4: ANDRÉ-QUILLEN (TAQ)
    % ------------------------------------------------
    \item \textbf{Level 4: Harrison / André-Quillen (Commutative)} \\
    \textit{Context:} Commutative ring spectrum $A$ ($E_\infty$-algebra). $M$ is an $A$-module.
    \begin{itemize}
        \item \textbf{Local System:} Related to the symmetric algebra structure (killing shuffles).
        \item \textbf{Homology (Cotangent Complex):}
        \[
        \operatorname{TAQ}_*(A; M) \cong \pi_* (M \wedge_A \mathbb{L}_{A}).
        \]
        Here $\mathbb{L}_A$ is the \textbf{Topological Cotangent Complex}. It classifies derivations: $\operatorname{Map}_{Mod_A}(\mathbb{L}_A, M) \simeq \operatorname{Der}(A, M)$.
        \item \textbf{Cohomology (Deformation Cohomology):}
        \[
        D^*(A; M) \cong \pi_{-*} \operatorname{RHom}_A(\mathbb{L}_A, M).
        \]
        Specifically classifies commutative deformations.
    \end{itemize}

    % ------------------------------------------------
    % LEVEL 5: FACTORIZATION
    % ------------------------------------------------
    \item \textbf{Level 5: Factorization Homology (Manifolds)} \\
    \textit{Context:} $E_n$-algebra $A$, Manifold $M$ of dimension $n$.
    \begin{itemize}
        \item \textbf{Local System:} The algebra $A$ assigned to disjoint disks.
        \item \textbf{Homology (The Integral):}
        \[
        \int_M A \simeq \operatorname{colim}_{\{U_1 \sqcup \dots \sqcup U_k \hookrightarrow M\}} (A(U_1) \otimes \dots \otimes A(U_k)).
        \]
        This is a colimit over the category of disk embeddings $\operatorname{Disk}(M)$.
        \item \textbf{Cohomology (Global Sections):}
        \[
        \oint^M A \simeq \lim_{U \hookrightarrow M} A(U).
        \]
        Often related to the mapping space $\operatorname{Map}(M, B^n A^\times)$ (Non-abelian cohomology).
    \end{itemize}

    % ------------------------------------------------
    % LEVEL 6: TOPOLOGICAL CYCLIC (TP)
    % ------------------------------------------------
    \item \textbf{Level 6: Topological Periodic / Cyclic (Tate)} \\
    \textit{Context:} $A$ is a ring spectrum. We use the $S^1$-action on $\operatorname{THH}(A)$.
    \begin{itemize}
        \item \textbf{Local System:} $S^1$-equivariant structure of $A$.
        \item \textbf{Homology (TP / Tate Construction):}
        \[
        \operatorname{TP}(A) \simeq (\operatorname{THH}(A))^{tS^1} \simeq \operatorname{Cofiber}\left( \operatorname{Nm}: \operatorname{THH}(A)_{hS^1} \to \operatorname{THH}(A)^{hS^1} \right).
        \]
        Defined as the Tate spectrum (mixing orbits and fixed points).
        \item \textbf{Cohomology (TC / Invariants):}
        \[
        \operatorname{TC}(A) \simeq \operatorname{Map}_{Sp^{S^1}}(S^0, \operatorname{THH}(A)) \quad (\text{Roughly}).
        \]
        Modern definition uses the fiber of the Frobenius map: $\operatorname{TC}(A) \simeq \operatorname{fib}(\operatorname{TR}(A) \xrightarrow{1-F} \operatorname{TR}(A))$.
    \end{itemize}

\end{enumerate}
\end{example}



\begin{remark}[The Operadic Unification and Geometric Duality]
The various homology and cohomology theories discussed above (Singular, Hochschild, André-Quillen, etc.) are strictly special cases of the general \textbf{Operadic Homology and Cohomology}. This framework unifies the algebraic machinery with the geometric intuition of the "Tangent Bundle" as follows:

\begin{enumerate}
    \item \textbf{The Tangent Structure (Beck Modules vs. $\operatorname{Tw}(\mathcal{C})$):}
    For an algebra over an arbitrary operad $\mathcal{O}$, the intrinsic "tangent bundle" is the category of \textbf{Beck Modules} over the universal enveloping algebra $U_{\mathcal{O}}(A)$.
    \begin{itemize}
        \item When $\mathcal{O} = Ass$ (Associative), the category of Beck Modules identifies with the category of \textbf{Bimodules} ($A \otimes A^{op}$-modules).
        \item Consequently, $\operatorname{Tw}(\mathcal{C})$ is precisely the geometric realization (the loop-like skeleton) of the Beck Module structure for associative algebras.
    \end{itemize}

    \item \textbf{The Generating Object (Cotangent Complex):}
    The linearization of the operadic structure yields the \textbf{Cotangent Complex} $\mathbb{L}_{A/\mathcal{O}}$. This object plays the role of the generic "1-form" ($\Omega^1$) on the algebraic variety defined by $A$.

    \item \textbf{Geometric Duality (HKR Correspondence):}
    All theories can be classified by their interaction with the Cotangent Complex, reflecting the duality between \textbf{Vector Fields} and \textbf{Differential Forms}:
    
    \begin{itemize}
        \item \textbf{Cohomology ($\operatorname{Ext} \leftrightarrow$ Vector Fields):}
        \[ H^*_{\mathcal{O}}(A, M) \cong \operatorname{Ext}^*_{U_{\mathcal{O}}(A)}(\mathbb{L}_{A/\mathcal{O}}, M) \]
        Geometrically, cohomology classifies \textbf{derivations} and \textbf{deformations}. Like a \textbf{Vector Field} (or Polyvector field), it describes the "directions" in which the algebraic structure can flow or be deformed (e.g., $H^2$ as deformation obstruction).

        \item \textbf{Homology ($\operatorname{Tor} \leftrightarrow$ Differential Forms):}
        \[ H_*^{\mathcal{O}}(A, M) \cong \operatorname{Tor}_*^{U_{\mathcal{O}}(A)}(\mathbb{L}_{A/\mathcal{O}}, M) \]
        Geometrically, homology measures the \textbf{volume} or \textbf{trace} of the structure. Like a \textbf{Differential Form}, it integrates the linearized structure (Cotangent Complex) over the fundamental cycle of the category (e.g., the circle $S^1$ in THH).
    \end{itemize}
\end{enumerate}

In summary, $\operatorname{Tw}(\mathcal{C})$ provides the \textit{integration domain} (geometry), the Local System provides the \textit{coefficients} (physics), and the Operadic type determines whether we are integrating forms (Homology) or solving for fields (Cohomology).

\end{remark}



\begin{remark}[\textbf{Unified Sheaf-Theoretic Perspective}]
The various homology and cohomology theories discussed can be unified as \textbf{Sheaf Cohomology} (for obstructions) and \textbf{Cosheaf Homology} (for traces) defined over distinct Grothendieck sites. In this view, algebra and geometry are distinguished only by the category on which the sheaf is defined.

\begin{enumerate}
    \item \textbf{The Site Definitions:}
    \begin{itemize}
        \item \textbf{Singular Theory:} Defined on the site of open sets of a topological space $X$.
        \item \textbf{Hochschild Theory:} Defined on the \textbf{Cyclic Site} (or $\text{Tw}(\mathcal{C})$), representing the geometry of the circle $S^1$.
        \item \textbf{Operadic Theory:} Defined on the \textbf{Dendroidal Site} $\Omega$ (Category of Trees), representing the geometry of branching operations.
    \end{itemize}

    \item \textbf{The Duality of Measurement:}
    \begin{itemize}
        \item \textbf{Cohomology ($H^* \simeq R\Gamma$):} Computes the derived global sections of a \textbf{Sheaf}. It classifies the \textbf{lifting obstructions} of local structures to global ones (e.g., $k$-invariants).
        \item \textbf{Homology ($H_* \simeq \mathbb{L}\operatorname{colim}$):} Computes the derived colimit of a \textbf{Cosheaf}. It measures the \textbf{global trace} or "volume" of the algebraic structure (e.g., Factorization Homology).
    \end{itemize}
\end{enumerate}

Any "twisting" in the theory is simply the non-triviality of the coefficient sheaf (Local System) over the respective site.

\end{remark}

\begin{definition}[\textbf{Universal Monodromy Object via Geometric Tannaka Duality}]
Let $\mathcal{X}$ be an $\infty$-topos and let $\operatorname{Loc}(\mathcal{X})$ denote the $\infty$-category of local systems on $\mathcal{X}$ (valued in the category of spaces $\mathcal{S}$).

The \textbf{Universal Monodromy Object} of $\mathcal{X}$, formally known as the \textbf{Fundamental $\infty$-Groupoid} or \textbf{Shape} $\Pi_{\infty}(\mathcal{X})$, is defined as the unique object in $\mathcal{S}$ determined by the following equivalence of $\infty$-categories:
\[
\operatorname{Loc}(\mathcal{X}) \xrightarrow{\sim} \operatorname{Fun}(\Pi_{\infty}(\mathcal{X}), \mathcal{S}).
\]
\textbf{Interpretation as Tannaka Duality:}
This definition is an instance of \textbf{Geometric Tannaka Duality}. Here, $\operatorname{Loc}(\mathcal{X})$ serves as the "category of representations," and $\Pi_{\infty}(\mathcal{X})$ is the "group" (or groupoid) reconstructed from these representations. 
Thus, $\Pi_{\infty}(\mathcal{X})$ is the universal source of monodromy: to give a local system on $\mathcal{X}$ is equivalent to giving a monodromy representation of $\Pi_{\infty}(\mathcal{X})$.
\end{definition}




\begin{example}[\textbf{Construction of the Twisted Postnikov Tower}]
Let $X$ be a path-connected CW-complex. We define the Postnikov tower $\{P_n(X)\}$ inductively. The construction relies on the definition of local coefficient systems and the pullback of the universal path fibration.

\vspace{0.5em}
\noindent\textbf{1. The Coefficient Functor $\underline{\pi}_n$} \\
The $n$-th homotopy group is defined as a functor from the fundamental groupoid of $X$ to the category of abelian groups:
\[
\underline{\pi}_n: \Pi_1(X) \longrightarrow \mathbf{Ab}.
\]
This functor is specified by the following data:
\begin{itemize}
    \item \textbf{Objects:} For each $x \in X$, $\underline{\pi}_n(x) := \pi_n(X, x)$.
    \item \textbf{Morphisms:} For each path class $[\gamma]: x \to y$, the map $\underline{\pi}_n([\gamma])$ is the change-of-basepoint isomorphism $\gamma_\#: \pi_n(X, x) \to \pi_n(X, y)$ induced by path lifting.
\end{itemize}
This functor $\underline{\pi}_n$ constitutes the local system of coefficients required for the subsequent cohomology groups.

\vspace{0.5em}
\noindent\textbf{2. The k-invariant and Pullback Definition} \\
The transition from the $(n-1)$-th stage to the $n$-th stage is determined by the $k$-invariant, a cohomology class $k_{n+1} \in H^{n+1}(P_{n-1}(X); \underline{\pi}_n)$. This class is represented by a continuous map:
\[
k_{n+1}: P_{n-1}(X) \longrightarrow K(\underline{\pi}_n, n+1),
\]
where $K(\underline{\pi}_n, n+1)$ is the classifying space for the twisted cohomology (a fibration over $K(\pi_1(X), 1)$).

We define $P_n(X)$ as the pullback of the universal path space $\mathcal{P}K(\underline{\pi}_n, n+1)$ along the map $k_{n+1}$. Formally, we write:
\[
P_n(X) := k_{n+1}^* \bigl( \mathcal{P}K(\underline{\pi}_n, n+1) \bigr).
\]
This definition identifies $P_n(X)$ with the limit of the following cospan diagram:
\[
\begin{tikzcd}[row sep=large, column sep=large]
P_n(X) \arrow[r] \arrow[d, "p_n"'] \arrow[dr, phantom, "\lrcorner", very near start] & \mathcal{P}K(\underline{\pi}_n, n+1) \arrow[d] \\
P_{n-1}(X) \arrow[r, "k_{n+1}"'] & K(\underline{\pi}_n, n+1)
\end{tikzcd}
\]
Here, $\mathcal{P}K(\underline{\pi}_n, n+1)$ is the contractible path space of the twisted Eilenberg-MacLane space. The resulting space $P_n(X)$ is the total space of a fibration over $P_{n-1}(X)$ with fiber $K(\pi_n, n)$, where the twisting is fully encoded by the map $k_{n+1}$.
\end{example}



\begin{remark}[\textbf{Operations as Monodromy via Spectral Sequence Dynamics}]
The diverse zoology of homotopy operations can be unified as manifestations of \textit{Universal Monodromy} within the differential dynamics ($d_r$) and multiplicative structures of specific spectral sequences. Each operation represents an obstruction or a higher-order coherence constraint.

\begin{itemize}
    \item \textbf{Geometric Monodromy (Serre \& EHP Spectral Sequences):}
    The \textbf{Serre SS} (for a fibration $F \to E \to B$) encodes the twisting of the fiber over the base.
    \begin{itemize}
        \item The \textbf{Transgression} is realized as the differential $d_n: E_n^{0, n-1} \to E_n^{n, 0}$, representing the obstruction to extending a class from the fiber to the total space.
        \item \textbf{k-invariants} appear as the first non-trivial differentials in the spectral sequence of the Postnikov tower, explicitly measuring the twisting of the fibration.
        \item The \textbf{Hurewicz map} sits on the edge homomorphisms, relating homotopy (fiber) to homology (total space).
        \item \textbf{Whitehead products} are detected by differentials in the \textbf{EHP spectral sequence} (or Serre SS of wedge sums), measuring the failure of the sphere spectrum to be commutative.
    \end{itemize}

    \item \textbf{Algebraic Monodromy (Eilenberg-Moore \& Bockstein Spectral Sequences):}
    \begin{itemize}
        \item The \textbf{Cup Product} and \textbf{Pontryagin Product} constitute the multiplicative structure of the $E_2$ page in the Cohomology and Homology \textbf{Serre SS}, respectively.
        \item The \textbf{Bockstein Operation} ($\beta$) is the differential $d_1$ of the \textbf{Bockstein SS} associated with the extension $0 \to \mathbb{Z}/p \to \mathbb{Z}/p^2 \to \mathbb{Z}/p \to 0$.
        \item \textbf{Samelson} and \textbf{Browder brackets} appear as commutator obstructions in the spectral sequences governing H-spaces and loop spaces.
    \end{itemize}

    \item \textbf{Stable \& Higher Monodromy (Adams \& Adams-Novikov Spectral Sequences):}
    These spectral sequences converge to stable homotopy groups, where the filtration degree corresponds to the "resolution depth."
    \begin{itemize}
        \item \textbf{Steenrod Operations} and \textbf{Dyer-Lashof Operations} act on the $E_2$ page of the \textbf{Adams SS}, encoding the internal symmetry of the coefficients ($\mathbb{F}_p$).
        \item \textbf{Landweber-Novikov Operations} play the analogous role in the \textbf{Adams-Novikov SS} (based on $MU$).
        \item \textbf{Massey Products} on the $E_r$ page converge to \textbf{Toda Brackets} in the stable homotopy groups. These represent higher-order obstructions ("ghosts" of vanished lower differentials).
        \item \textbf{Functional Cohomology Operations} arise as secondary differentials when primary operations (primary monodromy) vanish.
    \end{itemize}
\end{itemize}
In summary, all these operations are residues of the \textbf{Universal Monodromy}. They are detected either as the \textit{source} of a differential (an obstruction) or as the \textit{result} of a convergence (a higher composition), dictating how local algebraic data is glued into a global geometric structure.
\end{remark}


\begin{remark}[\textbf{Taxonomy of Spectral Sequences and the Unification via Monodromy}]
It is illuminating to classify spectral sequences into three fundamental types, each corresponding to a distinct strategy of decomposition in homotopy theory. Despite their differences, they share a common cohomological essence.

\begin{enumerate}
    \item \textbf{Geometric Filtration (Geometric Decomposition):}
    \begin{itemize}
        \item \textit{Examples:} Serre, Leray, EHP spectral sequences.
        \item \textit{Mechanism:} Corresponds to a decomposition of the \textbf{domain space} (e.g., via a CW-skeleton or a fiber bundle $F \to E \to B$).
        \item \textit{Philosophy:} We reconstruct the global topology by gluing local spatial slices (fibers).
    \end{itemize}

    \item \textbf{Resolution Filtration (Algebraic Decomposition):}
    \begin{itemize}
        \item \textit{Examples:} Adams, Adams-Novikov, Eilenberg-Moore spectral sequences.
        \item \textit{Mechanism:} Corresponds to a decomposition of the \textbf{category/structure} (e.g., resolving a spectrum by Eilenberg-MacLane spectra or free modules).
        \item \textit{Philosophy:} We reconstruct the stable homotopy type by gluing algebraic layers (resolutions).
    \end{itemize}

    \item \textbf{Coefficient Filtration (Numerical Decomposition):}
    \begin{itemize}
        \item \textit{Examples:} Bockstein spectral sequence.
        \item \textit{Mechanism:} Corresponds to a decomposition of the \textbf{codomain/values} (e.g., $0 \to \mathbb{Z}/p \to \mathbb{Z}/p^2 \to \dots$).
        \item \textit{Philosophy:} We refine the precision of the invariants by gluing value ranges.
    \end{itemize}
\end{enumerate}
\end{remark}


\begin{remark}[\textbf{Spectral Sequences as Sheaf Cohomology and Operational Monodromy}]
Fundamentally, the computation of a spectral sequence is the computation of \textbf{Sheaf Cohomology}. The $E_2$-page, typically of the form $H^p(B; \mathcal{H}^q(F))$, calculates the cohomology of the base with coefficients in the \textbf{local system} determined by the fiber.

In this framework, \textbf{Monodromy} transcends the classical role of $\pi_1$-action; it becomes the universal source of all \textbf{non-trivial twisted operations}.
\begin{itemize}
    \item \textbf{The Setup ($E_2$):} The local system itself encodes the "static" twist (the geometric monodromy).
    \item \textbf{The Dynamics ($d_r$ \& Operations):} The higher differentials and associated cohomology operations (such as \textbf{Steenrod squares}, \textbf{Massey products}, \textbf{Toda brackets}, and \textbf{k-invariants}) are the dynamic manifestations of this twist.
\end{itemize}
These operations quantify the obstruction to extending local sections to global ones. Specifically, phenomena like the \textbf{Bockstein} or \textbf{Transgression} arise precisely because the coefficient sheaf is not constant (or the filtration does not split). Thus, every non-trivial operation listed previously is essentially a measurement of the \textit{failure} of the global structure to be a simple product, a failure dictated entirely by the underlying Monodromy.
\end{remark}

\begin{remark}[\textbf{Stability as Linearized Monodromy}]
The essence of a \textbf{stable object} is that it embodies the \textbf{linearization} of Universal Monodromy.

Unlike unstable spaces where gluings are geometrically "curved," stable objects reside in an \textbf{additive category} where finite products and coproducts coincide ($X \times Y \simeq X \vee Y$). Consequently:
\begin{itemize}
    \item \textbf{Linearization:} The Monodromy action transforms from a non-linear geometric diffeomorphism into a linear algebraic operator.
    \item \textbf{Extension vs. Twisting:} The geometric "twisting" of a bundle simplifies to an algebraic \textbf{extension class} (in $\operatorname{Ext}$ groups).
\end{itemize}
Physically, if unstable homotopy theory studies the global manifold, stable homotopy theory studies its \textbf{tangent space}.
\end{remark}



\begin{remark}[\textbf{Differentials as Monodromy Residues in the Rees Algebra}]
The Rees algebra perspective offers a rigorous algebraic geometry for spectral sequences, framing the differential $d_r$ as the \textbf{residue} of the underlying Monodromy.

Let $(C, \partial, F^\bullet)$ be a filtered complex. The Rees algebra $\mathcal{R}(C) = \bigoplus_p F^p C \cdot t^{-p}$ encodes the filtration as a graded module over $k[t]$. We view $t$ as a deformation parameter where $t=0$ corresponds to the associated graded object ($E_1$ page) and $t=1$ to the total filtered complex.

\begin{enumerate}
    \item \textbf{The Expansion of the Boundary Operator:}
    Within the Rees algebra, the boundary operator $\partial$ does not simply commute with $t$. Instead, the interaction between the topology ($\partial$) and the filtration ($t$) can be expanded as a formal series. If $x \in F^p C$, the condition that $x$ survives to the $r$-th page means that its boundary is "deep" in the filtration:
    \[
    \partial x \in F^{p+r} C.
    \]
    
    \item \textbf{The Differential as a Residue:}
    In terms of the Rees algebra elements $\tilde{x} = x t^{-p}$, this condition translates to the equation:
    \[
    \partial_{\mathcal{R}}(\tilde{x}) = t^r \cdot \tilde{y}
    \]
    Here, the power $t^r$ measures the "distance" or "twist" between the filtration levels. The differential $d_r$ is precisely the operator that extracts the coefficient $\tilde{y}$ modulo $t$:
    \[
    d_r([x]) \equiv \text{Coeff}_{t^r}(\partial_{\mathcal{R}}(\tilde{x})) \pmod t.
    \]
    
    \item \textbf{Interpretation:}
    Thus, $d_r$ acts as a \textbf{Residue of the Monodromy}.
    \begin{itemize}
        \item The \textbf{Monodromy} is the global incompatibility between the filtration and the boundary operator as we deform from $t=0$ to $t=1$.
        \item The spectral sequence is the Taylor expansion of this Monodromy.
        \item The differential $d_r$ is the \textbf{first non-vanishing term} (the leading residue) in this expansion. It detects exactly where the "local" algebraic structure ($E_r$) fails to extend "globally" to the next order of precision ($E_{r+1}$), blocked by the twist of the bundle.
    \end{itemize}
\end{enumerate}
\end{remark}

\endgroup