
\section{Introduction}

The coherent--constructible correspondence is a bridge between two different
types of sheaf theories. On one side, one studies equivariant coherent sheaves
on a toric variety. On the other side, one studies constructible sheaves on a
real vector space, with singular support restricted by a conic subset determined
by the fan. The main point of the correspondence is that the algebraic and
equivariant data of a toric variety can be translated into polyhedral and
microlocal data on the constructible side.

The main goal of this paper is to explain and prove the coherent--constructible
correspondence for smooth toric varieties. More precisely, if \(X_\Sigma\) is a
smooth toric variety with acting torus \(T\), character lattice \(M\), and fan
\(\Sigma\subset N_{\mathbb R}\), then the correspondence takes the form of a
quasi-equivalence of dg categories
\[
\kappa_\Sigma:\mathrm{Perf}_T(X_\Sigma)
\overset{\sim}{\longrightarrow}
Sh_{\Lambda_\Sigma}(M_{\mathbb R}).
\]
Here \(\mathrm{Perf}_T(X_\Sigma)\) is the dg category of \(T\)-equivariant
perfect complexes on \(X_\Sigma\), and \(Sh_{\Lambda_\Sigma}(M_{\mathbb R})\)
is the dg category of constructible sheaves on \(M_{\mathbb R}\) whose singular
support is contained in the FLTZ skeleton \(\Lambda_\Sigma\). The FLTZ skeleton
is a conic subset of \(T^*M_{\mathbb R}\) defined directly from the fan
\(\Sigma\).

The proof used in this paper follows the standard generator strategy. On the
coherent side, one introduces theta objects
\[
\Theta'(\sigma,\chi)=(i_\sigma)_*\mathcal O_{U_\sigma}(\chi),
\]
where \(U_\sigma\) is the affine toric chart associated to a cone
\(\sigma\in\Sigma\). On the constructible side, one introduces the corresponding
theta sheaves
\[
\Theta(\sigma,\chi)
=
(i_{\chi+\sigma^\vee})_*\omega_{\chi+\sigma^\vee}.
\]
The functor \(\kappa_\Sigma\) is characterized by sending coherent theta objects
to constructible theta sheaves:
\[
\Theta'(\sigma,\chi)\longmapsto \Theta(\sigma,\chi).
\]
The essential calculation is the comparison of Hom-complexes between these
generators. Both sides are controlled by the same polyhedral condition:
\[
\mathrm{RHom}(\Theta(\sigma,\chi),\Theta(\tau,\psi))
\simeq
\begin{cases}
k, & \chi+\sigma^\vee\subset \psi+\tau^\vee,\\
0, & \text{otherwise}.
\end{cases}
\]
On the coherent side, this same condition says that the corresponding
equivariant monomial map is regular. Once the Hom-complexes are identified and
the theta objects are shown to generate both categories, the quasi-equivalence
follows from the generator criterion.

The organization of the paper is as follows.

Section 2 recalls the symplectic background for toric varieties. We review
symplectic manifolds, Kähler forms, Hermitian line bundles, compact real tori,
and moment polytopes. This material is not part of the proof of the
coherent--constructible correspondence itself. Its role is to explain the
geometric background behind toric varieties and to prepare for the later
Fukaya-theoretic interpretation.

Section 3 fixes the categorical and sheaf-theoretic conventions. We recall dg
categories, perfect complexes, equivariant coherent sheaves, constructible
sheaves, singular support, and sheaves with prescribed singular support. These
notions provide the language in which the correspondence is stated and proved.
In particular, the proof is formulated at the dg categorical level so that
Hom-complexes, shifts, cones, and quasi-equivalences can be handled explicitly.

Sections 4, 5, and 6 form the main body of the paper. Readers who are already
comfortable with toric varieties, dg categories, constructible sheaves, and
singular support may start directly from Section 4. Section 4 describes the
coherent side of the correspondence. It recalls the description of
\(T\)-equivariant coherent sheaves on affine toric charts in terms of
\(M\)-graded modules, and it introduces the coherent theta generators
\(\Theta'(\sigma,\chi)\). Section 5 constructs the constructible side. It
defines the FLTZ skeleton, studies the singular support of polyhedral
costandard sheaves, and introduces the constructible theta sheaves
\(\Theta(\sigma,\chi)\). Section 6 proves the toric coherent--constructible
correspondence by matching the two families of theta generators and comparing
their Hom-complexes.

Section 7 is introductory and interpretive. It explains how the constructible
side of the correspondence can be viewed from the perspective of microlocal
sheaf theory and Fukaya categories. The section does not give an independent
construction of the Fukaya category. Instead, it explains how the FLTZ skeleton,
which appears as a singular-support condition on the constructible side, can
also be interpreted as a Lagrangian or stop condition in a cotangent bundle.

Section 8 gives explicit examples of the correspondence. The examples include
\(\mathbb A^1\), \(\mathbb P^2\), \(\mathbb P^1\times\mathbb P^1\),
Hirzebruch surfaces, and a toric del Pezzo surface. In each case, we compute
the fan, the FLTZ skeleton, the theta sheaves, and the Hom-complexes between
theta objects. These examples are intended to make the abstract generator
calculation concrete: equivariant monomial maps on the coherent side become
inclusions of polyhedral sheaves on the constructible side.

Section 9 is also introductory. It discusses several directions in which the
toric coherent--constructible correspondence can be generalized. We describe
the basic changes that occur for toric Deligne--Mumford stacks, toric
fibrations, and Fourier--Mukai transforms. The aim is not to prove these
generalizations in full detail, but to indicate how the same organizing ideas
persist: the combinatorial input is modified, the coherent category changes
accordingly, and the constructible side is still governed by microlocal
conditions and theta-type generators.



We use the standard notation of toric geometry. Let \(T\) be an algebraic torus
over \(\mathbb C\). We write
\[
N=\operatorname{Hom}(\mathbb C^*,T),
\qquad
M=\operatorname{Hom}(T,\mathbb C^*)
\]
for the cocharacter and character lattices. Thus
\[
M=\operatorname{Hom}_{\mathbb Z}(N,\mathbb Z).
\]
Their realifications are
\[
N_{\mathbb R}=N\otimes_{\mathbb Z}\mathbb R,
\qquad
M_{\mathbb R}=M\otimes_{\mathbb Z}\mathbb R.
\]
For a fan \(\Sigma\subset N_{\mathbb R}\), we denote by \(X_\Sigma\) the
associated toric variety. For a cone \(\sigma\in\Sigma\), the corresponding
affine toric chart is denoted by
\[
U_\sigma=\operatorname{Spec}\mathbb C[\sigma^\vee\cap M].
\]
The inclusion is written as
\[
i_\sigma:U_\sigma\hookrightarrow X_\Sigma.
\]

For a cone \(\sigma\), we write
\[
\sigma^\vee=\{m\in M_{\mathbb R}\mid \langle m,n\rangle\ge 0
\text{ for all }n\in\sigma\}
\]
for its dual cone, and
\[
\sigma^\perp=\{m\in M_{\mathbb R}\mid \langle m,n\rangle=0
\text{ for all }n\in\sigma\}
\]
for its annihilator. We also use
\[
M_\sigma=M/(\sigma^\perp\cap M).
\]
The FLTZ skeleton associated to \(\Sigma\) is
\[
\Lambda_\Sigma
=
\bigcup_{\sigma\in\Sigma}
\bigcup_{\chi\in M_\sigma}
(\chi+\sigma^\perp)\times(-\sigma)
\subset T^*M_{\mathbb R}.
\]

We write \(\mathrm{Perf}_T(X_\Sigma)\) for the dg category of
\(T\)-equivariant perfect complexes on \(X_\Sigma\), and
\(Sh_{\Lambda_\Sigma}(M_{\mathbb R})\) for the dg category of constructible
sheaves on \(M_{\mathbb R}\) with singular support contained in
\(\Lambda_\Sigma\). Derived Hom-complexes are denoted by \(\mathrm{RHom}\).




