{\begingroup
\renewcommand{\hom}{\operatorname{Hom}}
\newcommand{\ihom}{\operatorname{\underline{Hom}}}
\newcommand{\tr}{\operatorname{Tr}}
\newcommand{\ol}{\mathcal{O}_L}
\newcommand{\ok}{\mathcal{O}_K}
\newcommand{\ab}{\text{ab}}
\newcommand{\ov}{\mathcal{O}_v}
\newcommand{\cont}{\operatorname{cont}}
\renewcommand{\o}{\mathcal{O}}
\newcommand{\gal}{\operatorname{Gal}}
\newcommand{\dics}{\operatorname{dics}}
\newcommand{\br}{\operatorname{Br}}
\renewcommand{\det}{\operatorname{det}}
\renewcommand{\char}{\operatorname{char}}
\newcommand{\I}{\mathbb{I}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\p}{\mathfrak{p}}
\renewcommand{\d}{\mathfrak{d}}
\newcommand{\D}{\mathfrak{D}}
\renewcommand{\v}{\mathfrak{v}}
\newcommand{\f}{\mathfrak{f}}
\renewcommand{\a}{\mathfrak{a}}
\renewcommand{\b}{\mathfrak{b}}
\renewcommand{\P}{\mathfrak{P}}
\newcommand{\J}{\mathfrak{J}}
\newcommand{\N}{\operatorname{N}}
\newcommand{\Cl}{\operatorname{Cl}}
\newcommand{\legendre}[2]{\genfrac{(}{)}{}{}{#1}{#2}}
\newcounter{ant} 
\newcommand{\np}{\stepcounter{ant}\noindent\textbf{\arabic{ant}.}\quad}
\newcounter{prob} 
\newcommand{\prob}{\stepcounter{prob}\noindent\textbf{\arabic{prob}.}\quad}




\chapter{Algebraic Number Theory}
First let we consider some basic extensions:
\begin{itemize}
    \item[Type A] Quadratic Extensions $[L:K]=2$;
    \item[Type B] Cyclotomic Extensions $K(\zeta_n)/K$;
    \item[Type C] Kummer Extensions $L=K(\sqrt[n]{a})$;
    \item[Type D] Pure Cubic Extensions $L=K(\sqrt[3]{a})$;
    \item[Type E] Cyclic Cubic Extensions $\text{Gal}(L/K) \cong C_3$;
    \item[Type F] Biquadratic Extensions $L = K(\sqrt{a}, \sqrt{b})$;
    \item[Type G] Quaternion Extensions $\text{Gal}(L/K) \cong Q_8$;
    \item[Type H] Dihedral Extensions $\text{Gal}(L/K) \cong D_{2n}$;
    \item[Type I] Complex Multiplication Fields $L = \mathbb{Q}(\zeta_n + \zeta_n^{-1})$;
    \item[Type J] Eisenstein Extension $L =  \mathbb{Q}(\omega)$ where $\omega$ is a root of an Eisenstein polynomial.
    \item[Type K] Artin-Schreier Extensions $L = K(y)$ with $y^p - y = a\in K$.
\end{itemize}
For Type C, the base field $K$ must contains the roots of unity $\mu_n=\langle\zeta_n\rangle$.
For Type K, $\char(K)=p$.


Let us review concepts from  Algebraic Number Theory.

\section*{Lattice over Dedekind domain}

Lattice is the most important concept in Algebraic Number Theorem. Let we give some examples.
\begin{enumerate}
    \item $\ol$ as $\ok$-lattice equipped with with $\tr_{L/K}$ as the bilinear form.
    \item The Value Group $v(K^*)$ is a one-dimension lattice.
    \item $L\otimes_K K_v$ is a $K_v$-vector space.
    \item Residue Field $\kappa(\P)$ is a $\kappa(\p)$-vector space.
    \item The valuation of idele $\log(A_K^{\times})$ produces lattice structure.
    \item The Unit Lattice $\log:\ok^\times\to \R^{r_1+r_2}$ and Minkowski Lattice $\ok\to \R^{r_1}\times \C^{r_2}$.
\end{enumerate}

There are several important concepts about lattice over Dedekind domain.
\begin{definition}[Trace Ideal]
    The trace ideal $\mathfrak{T}_{L/K}$ is defined by scale ideal $\mathfrak{s}(\mathcal{O}_L) = \langle \text{Tr}_{L/K}(xy) \mid x,y \in \mathcal{O}_L \rangle_{\mathcal{O}_K}$.
\end{definition}

\begin{definition}[Discriminant of Field]
    The discriminant of field $L$ is given by $\dics(\langle\alpha_1,\dots,\alpha_n \rangle) = \det(\tr(\alpha_i\alpha_j))$ where $\{\alpha_i\}$ is an integral basis.
\end{definition}

\begin{definition}[Inverse Different and Different]
    The inverse different is given by the dual lattice $\ol^{\#}$. And the different $\D_{L/K}$ is $(\ol^{\#})^{-1}$.
\end{definition}

\begin{definition}[Different of an element]
    Let $L/K$ be a finitely algebraic extension with a minimal polynomial $f(x)$. Then the different of an element $\alpha$ is $f'(\alpha)\cdot \ol$.
\end{definition}

\begin{theorem}[Different Deduced by Different of Elements]
    We have an isomorphism 
    \begin{align*}
        \D_{L/K}\simeq  (f'(\alpha))_{\alpha\in L}
    \end{align*}
\end{theorem}

When $\ok$ is not PID, then $\ol$ is not a free $\ok$-module. In this situation, we use Steinitz class to delineate it.
\begin{theorem}[Steinitz Class]
    There exist a basis $\{e_1, \dots, e_n\}$ of $L$ over $K$ and fractional ideals $\mathfrak{a}_1, \dots, \mathfrak{a}_n$ of $\mathcal{O}_K$ such that:$$\mathcal{O}_L = \mathfrak{a}_1 e_1 \oplus \mathfrak{a}_2 e_2 \oplus \cdots \oplus \mathfrak{a}_n e_n$$Furthermore, for any non-zero $\mathcal{O}_L$-ideal $\mathfrak{I}$, there exist fractional ideals $\mathfrak{b}_1, \dots, \mathfrak{b}_n$ of $\mathcal{O}_K$ such that:$$\mathfrak{I} = \mathfrak{b}_1 e_1 \oplus \mathfrak{b}_2 e_2 \oplus \cdots \oplus \mathfrak{b}_n e_n.$$
\end{theorem}

\begin{definition}[Norm and Discriminant of an Ideal]
    The norm of an ideal $\J$ is given by 
    \begin{align*}
        \N_{L/K}(\J) = \frac{\b_1\cdots \b_n}{\a_1\cdots \a_n}.
    \end{align*}
    The Discriminant of it is given by 
    \begin{align*}
        \d(\J) = \det(\tr_{L/K}(e_ie_j))\cdot {(\b_1\cdots \b_n)^2}.
    \end{align*}
   Actually, it is just the volume as an $\ok$-lattice. 
\end{definition}

\begin{theorem}[Relation of Different and Discriminant]
    We have an isomorphism 
    \begin{align*}
        \d_{L/K} = \N_{L/K}(\D_{L/K}).
    \end{align*}
\end{theorem}

\begin{theorem}[Discriminant of an order]
    $$(\Delta_{L/K}(\theta)) = [\mathcal{O}_L : \mathcal{O}_K[\theta]]_{\mathcal{O}_K}^2 \cdot \Delta_{L/K}$$
\end{theorem}


\begin{definition}[Conductor of an Order]
    Given an order $\o$, its conductor is given by 
    \begin{align*}
        \f(\o) = \{x\in \ok| x\cdot \ok \in \o\}.
    \end{align*}
\end{definition}

\begin{theorem}[Resultant and Field Norm for Non-Monic Minimal Polynomials]
Let $K = \mathbb{Q}(\alpha)$ be a number field of degree $n$, and let

\[
f(x) = a_n x^n + a_{n-1} x^{n-1} + \cdots + a_0 \in \mathbb{Z}[x]
\]
be the minimal polynomial of $\alpha$ over $\mathbb{Q}$ with leading coefficient $a_n \neq 0$.
Let $g(x) \in \mathbb{Q}[x]$ be a polynomial of degree $m$, and set $\beta = g(\alpha) \in K$.

Then the field norm of $\beta$ over $\mathbb{Q}$ satisfies

\[
N_{K/\mathbb{Q}}(\beta) = \frac{1}{a_n^m} \,\mathrm{Res}(f, g),
\]
where $\mathrm{Res}(f, g)$ denotes the resultant of $f$ and $g$.
\end{theorem}



\section*{Valuation}




\np Consider algebraic number field $L/\Q$. Let $\p$ lies over $p$. Then we have the ideal norm
\begin{align*}
    N(\p) = [\ol:\p] = \det(\p/\ol) = p^{f(\p)}.
\end{align*}
where $f(\p)$ is inertia degree.

\section*{Local to Global Principle}

Consider algebraic field extension $L/K$ with a valuation $v$ of $K$.
Moreover we require $L/K$ is finite and seperable.
The Local-to-Global Principle is basically consider the $K$-embedding to $\bar{K}_v$ of $L$.
Given by an embedding $\sigma:L\to \bar{K}_v$, we then have an induced valuation $w_{\sigma}:=\bar{v}\circ\sigma$ where $\bar{v}$ is uniquely determined by $v$ since $K_v$ is Henselian.
We let $L_{w}$ denote the completion of $L$ corresponding to the valuation $w$.


There are some facts about this process.

\np Every extension $w$ of $v$ is identified with $\bar{v}\circ \sigma$ for a embedding $\sigma$.

\np Two extension $\bar{v}\circ \sigma$ and $\bar{v}\circ \sigma'$ are equal if and only if $\sigma$ and $\sigma'$ are conjugate over $K_v$.

\np Suppose that $L=K(\alpha)$ with minimal polynomial $f(x)$. Then the extensions of valuation are 1-1 corresponds to the irreducible factors $f_i$ in 
\begin{align*}
    f(x) = f_1(x)\dots f_n(x)
\end{align*}
of $f$ over $K_v$.

\np we have a useful fact that 
\begin{align*}
L\otimes K_v\simeq K[x]/f(x)    \otimes_K K_v\simeq K_v[x]/f(x)\simeq \prod_{w|v} K_v[x]/f_w(x)\simeq  \prod_{w|v} L_w.
\end{align*} 
We should notice that the decomposition $f(x)=\prod f_w(x)$ relies on seperality of $L/K$.

\np We also have the norm and trace formula 
\begin{align*}
    \N_{L/K}(\alpha) = \prod_{w|v} \N_{L_w/K_v}(\alpha) \text{ and }  \tr_{L/K}(\alpha) = \sum_{w|v}\tr_{L_w/K_v}(\alpha).
\end{align*}


\section*{Newton Polygon and Hensel's Lemma}
\begin{definition}[Newton Polygon]
Let $K$ be a field with a discrete valuation $v$, and let

\[
f(x) = a_0 + a_1 x + a_2 x^2 + \cdots + a_n x^n \in K[x]
\]
be a polynomial with $a_0, a_n \neq 0$. The \emph{Newton polygon} of $f$ 
with respect to $v$ is the lower convex hull of the set of points

\[
\bigl\{ (i, v(a_i)) : 0 \leq i \leq n,\ a_i \neq 0 \bigr\} \subset \mathbb{R}^2.
\]
\end{definition}
\begin{theorem}[Newton Polygon Decomposition]
Let $(K, v)$ be a Henselian valued field and $f(x) \in K[x]$ a monic 
polynomial. Suppose the Newton polygon of $f$ consists of segments with 
slopes $-\lambda_1 < -\lambda_2 < \cdots < -\lambda_r$ and horizontal 
lengths $\ell_1, \ell_2, \ldots, \ell_r$. Then $f$ factors uniquely in 
$K[x]$ as

\[
f(x) = f_1(x) \cdot f_2(x) \cdots f_r(x),
\]
where each $f_i(x) \in K[x]$ is monic of degree $\ell_i$, and every root 
of $f_i$ in $\overline{K}$ has valuation $\lambda_i$.
\end{theorem}

\begin{lemma}[Hensel's Lemma]
If a primitive polynomial $f(x) \in \mathcal{O}[x]$ admits modulo $\mathfrak{p}$ 
a factorization

$$
f(x) \equiv \bar{g}(x)\bar{h}(x) \bmod \mathfrak{p}
$$
into relatively prime polynomials $\bar{g}, \bar{h} \in \kappa[x]$, then $f(x)$ 
admits a factorization

$$
f(x) = g(x)h(x)
$$
into polynomials $g, h \in \mathcal{O}[x]$ such that $\deg(g) = \deg(\bar{g})$ and

$$
g(x) \equiv \bar{g}(x) \bmod \mathfrak{p} \quad \text{and} \quad 
h(x) \equiv \bar{h}(x) \bmod \mathfrak{p}.
$$
\end{lemma}

There is a very useful corollary about Hensel's lemma.
\begin{corollary}[Lift of Simple root]
    Suppose that $K$ is a henselian field with a valuation $v$. Let $\kappa(\p)$ denote the residue field of $\ov$.
    Let $f(x)\in\ov[x]$ and $\bar{f} = f\bmod\p$.
    If there exists $\bar{a}\in\kappa(\p)$ such that 
    \begin{align*}
        \bar{f}(\bar{a}) = 0 \text{ and } \bar{f}'(\bar{a}) \neq 0.
    \end{align*}
    Then there exists a unique lift $a\in\ov$ such that $\bar{a} = a\bmod \p$ and $f(a)=0$.
\end{corollary}

\begin{theorem}[Dumas's Criterion]
Let $K$ be a field equipped with a discrete valuation $v$. Let 
\[
    f(x) = a_n x^n + a_{n-1}x^{n-1} + \dots + a_1 x + a_0 \in K[x]
\]
be a polynomial of degree $n$ with $a_n a_0 \neq 0$. 
If the Newton polygon of $f(x)$ consists of a single line segment connecting the points $(0, v(a_0))$ and $(n, v(a_n))$, and if the horizontal length and vertical length of this segment are coprime, i.e.,
\[
    \gcd(n, |v(a_n) - v(a_0)|) = 1,
\]
then $f(x)$ is irreducible over $K$.
\end{theorem}





\section*{Ramification}
\begin{definition}[Tamely Ramification]
    We call $\P$ is tamely ramified over $\p$ if $\kappa(\P)/\kappa(\p)$ is seperable and  $\text{gcd}(e(\P/\p),\char(\kappa(\p)))=1$.
\end{definition}
 

We give a equivalent describtion when $K$ is Henselian.
\begin{theorem}[Tamely Ramification]
    A finite extension $L|K$ is tamely ramified if and only if the extension 
$L|T$ is generated by radicals

\[
L = T\!\left(\sqrt[m_1]{a_1},\, \ldots,\, \sqrt[m_r]{a_r}\right)
\]
such that $(m_i, p) = 1$. In this case the fundamental identity always holds:

\[
[L : K] = ef.
\]
\end{theorem}


\begin{proposition}[Different and Tame Ramification]
Let $L|K$ be a finite separable extension of Henselian fields.
 Then

\[
v_L(\mathfrak{d}_{L|K}) \geq e - 1,
\]
with equality if and only if $\mathfrak{P}/\mathfrak{p}$ is tamely ramified:

\[
\mathfrak{P}/\mathfrak{p} \text{ is tamely ramified} 
\iff v_L(\mathfrak{d}_{L|K}) = e - 1.
\]
Equivalently, in terms of ideals,

\[
\mathfrak{d}_{L|K} = \mathfrak{P}^{e-1} 
\iff \mathfrak{P}/\mathfrak{p} \text{ is tamely ramified}.
\]
In the wildly ramified case, $v_L(\mathfrak{d}_{L|K}) \geq e$.
\end{proposition}


\begin{proposition}[Trace and Tame Ramification]
    The extension is tamely ramified if and only if the trace ideal $\mathfrak{T}_{L/F} = \ok$.
\end{proposition}

\begin{theorem}[Dedekind-Kummer Theorem]
    Assume $L = K(\alpha)$ and $\alpha \in \ol$, let $f \in \ok[x]$ be the minimal polynomial of $\alpha$.
    Assume that $\char(\kappa(\p))\nmid N(\ok[\alpha])$. Suppose $g_1, \dots, g_r \in \ok[x]$ are monic polynomials for which
\[
\bar{f} = \bar{g}_1^{e_1} \cdots \bar{g}_r^{e_r}
\]
is a complete factorization of $\bar{f} \in (\ok/\mathfrak{p})[x]$, where $\bar{\cdot}$ denotes reduction modulo $\mathfrak{p}$, and let $\mathfrak{q}_i := (\mathfrak{p}, g_i(\alpha))$ be the $\ol$-ideal generated by $\mathfrak{p}$ and $g_i(\alpha)$. Then
\[
\mathfrak{p}\ol = \mathfrak{q}_1^{e_1} \cdots \mathfrak{q}_r^{e_r},
\]
is the prime factorization of $\mathfrak{p}\ol$ in $\ol$ and the residue degree of $\mathfrak{q}_i$ is $f_i := \deg g_i$.

\end{theorem}

The condition $\char(\kappa(\p))\nmid N(\ok[\alpha])$ holds iff. any prime ideal $\P$ lying over $\p$ not contains conductor $\f$.
Therefore we have 
\begin{align*}
    \ol\otimes_{\ok} \o_{K,\p} \simeq \ok[\alpha]\otimes_{\ok} \o_{K,\p}
\end{align*}
Tensor product each side by $\hat{\o}_{K,\p}$, then we obtain that
\begin{align*}
    \ol\otimes_{\ok} \hat{\o}_{K,\p}\simeq \ok[\alpha]\otimes_{\ok}  \hat{\o}_{K,\p} \simeq  \hat{\o}_{K,\p}[x]/f(x).
\end{align*}
Since $ \hat{\o}_{K,\p}$ shares the same residue field with $\ok$ over $\p$, the decomposition of $\bar{f}$ then can be lift to the 
local ring $\hat{\o}_{K,\p}$. 
Using CRT on the right hand side, we then have 
\begin{align*}
    \ol\otimes_{\ok}  \hat{\o}_{K,\p}\simeq \prod_{i=1}^{r}  \hat{\o}_{K,\p}[x]/(g_i^{e_i})
\end{align*}
There for we just need to consider the decomposition of $\p$ on each $\hat{\o}_{K,\p}[x]/(g_i^{e_i})$.





maximal unramif
Kummer Theory
\section*{Ideal Class Group}

We consdier algebraic number field $L/\Q$.

\np The Minkowski embedding just given by canonical embedding $L\to L\otimes \R$.
Given a primitive element and minimal polynomial, it can be explicitly described by 
\begin{align*}
    \R[x]/f(x) \simeq \bigoplus_{i=1}^{r_1} \R[x]/(x-{a_i}) \oplus \bigoplus_{j=1}^{r_2} \R[x]/(x^2+b_jx+c_j) = \bigoplus_{i=1}^{r_1} \R \oplus \bigoplus_{j=1}^{r_2} \C
\end{align*}
Therefore, the image of the ring of integers $\mathcal{O}_L$ under this embedding forms a $\mathbb{Z}$-lattice of rank $r_1 + 2r_2$ inside this space.

\np Dirichlet Unit Theorem: $K^*\simeq \pi(K)\times \mathbb{Z}^{r_1+r_2-1}$.

\np The Minkowski constant of $L$ is given by 
\begin{align*}
    M(L) = (\frac{4}{\pi})^{r_2}\frac{n!}{n^n}|d(K)|^{1/2}
\end{align*}

A quick method to find the roots of unity for $\ok$. Consider $\p$ is a prime ideal with residue field $\F_q$. Then the canonical isomorphism impose that 
\begin{align*}
    |W_K|\mid  q-1.
\end{align*}
Therefore, we can find some prime ideals to minimize our search.


\section*{Hilbert's Ramification Tower}

\begin{definition}[Decomposition Group and Decomposition Field]
    If $\P$ is a prime ideal of $\o$, then the subgroup 
    \begin{align*}
        G_\P =\{\sigma|\sigma(\P)=\P\}
    \end{align*}
    is called the decomposition group of $\P$ over $K$. The fixed field $Z_\P$ is called the decomposition field. 
\end{definition}

\begin{definition}[Inertia Group and Inertia Field]
    The Inertia group of $\P$ is given by the kernel of homomorphism
    \begin{align*}
        G_\P \to G(\kappa(\P)/\kappa(\p)).
    \end{align*}
    The fixed field $I_\P$ is called the inertia field. 
\end{definition}

We have a tower of field extension by 
\begin{align*}
    K\xrightarrow{\text{split}} Z_\P \xrightarrow{\text{inertia extension}} T_\P \xrightarrow{\text{ramification}} L
\end{align*}

If $L/K$ is unramified, it means that $I_\P$ is trivial and thus we have an isomorphism 
\begin{align*}
    G_\P \simeq G(\kappa(\P)/\kappa(\p))
\end{align*}

\begin{definition}[Frobenius Element]
    Let $L/K$ be a Galois extension of number fields, and let $\mathfrak{P}$ be a prime of $L$ lying over $\mathfrak{p}$ of $K$. Assume $\mathfrak{P}$ is unramified over $\mathfrak{p}$. The Frobenius element $\text{Frob}_{\mathfrak{P}}$ is the unique element in the Galois group $\text{Gal}(L/K)$ such that for all $\alpha \in \mathcal{O}_L$:$$\text{Frob}_{\mathfrak{P}}(\alpha) \equiv \alpha^{N_{K/\Q}(\mathfrak{p})} \pmod{\mathfrak{P}}$$
\end{definition}

The frobenius map of residue field over $\P$ is defined by $x\mapsto x^{N_{K/\Q}(\p)}$ since we want to fix the base field $K$.


\section*{Calssification of extension over a local field}

Suppose we consider the algebraic extension $L/\Q_p$ with degree $n$. 
The degree admits an decomposition 
    \begin{align*}
        n=  f \cdot e_0 \cdot p^k.
    \end{align*} 

The inertia degree $f$ corresponds unramified extensions $L^{\text{umf}}/\Q_p$. And we have 
\begin{align*}
    L^{\text{umf}}=\Q_p(\zeta_{p^f-1}).
\end{align*}
It is uniquely determined.

The tamely ramified index $e_0$ corresponds tamely ramified extensions $L^{1}/L^{\text{umf}}$. It has the form 
\begin{align*}
    L^{1} \simeq L^{\text{umf}}(\sqrt[e_0]{\pi})
\end{align*}
where $\pi$ is the uniformizer of $L^{\text{umf}}$. If $L^{\text{umf}}=\Q_p$, the uniformizer is exactly $p$.

The residue index $p^k$ corresponds wild ramified extensions $L/L^1$.

Actually, we can see more explicitly from the decomposition 
\begin{align*}
    \Q_p^\times\simeq \Z \times \Z^\times_p \simeq \Z\times (1+p\Z_p) \times \mu_{p-1}
\end{align*}

This decomposition is conisder by canonical homomorphism 
\begin{align*}
    \Z_p \to \F_p
\end{align*}
which induces 
\begin{align*}
    \Z_p^\times/(1+p\Z_p) \simeq \F_p^\times.
\end{align*}




\section*{Class Field Theory}



\begin{definition}[Local Artin Map]
    Let $K$ be a local field,then there is a canonical homomorphism
    \begin{align*}
        \theta_{K}: K^\times \to \gal(K^\ab/K).
    \end{align*}
    where $K^\ab$ denotes the maximal abelian extension of $K$.
\end{definition}
The general construction of local artin map is quite complicated. Mainly, it has two different way. The one is Lubin-Tate formal group and the other is 
Tate cohomology. We focus on cohomological way later.


Now let we consider a finite abelian extension $L/K$ over local field $K$. The Artin map induces a canonical epimorphism
\begin{align*}
    \theta_{L/K}: K^\times \to \gal(L/K).
\end{align*}
with kernel $N_{L/K}(K^\times)$. Therefore, we have an isomorphism 
\begin{align*}
    K^\times/N_{L/K}(L^\times)\simeq  \gal(L/K).
\end{align*}


\begin{definition}[Idele and Idele class group]
    The Idele group of a field $V$ is defined by 
$$\mathbb{I}_L = \prod_{v} \nolimits' L_v^\times = \{ (\alpha_v)_{v} \mid  \text{ All but finitely many } \alpha_v \in \o_v^\times \}.$$
Idele class group $C_L$ is defined by $\I_L/L^\times$.
\end{definition}

If we consider the field extension $L/K$, then we have 
$$\mathbb{I}_L = \prod_{v}\nolimits' \left( \prod_{w|v} L_w^\times \right)$$

\begin{definition}[Global Artin Map]
    The global artin map of a global field $K$ is given by 
    \begin{align*}
        \theta_K : \I_K &\to \gal(K^{\ab}/K)\\
        (\alpha_v)_v&\mapsto \prod_{v}\theta_{K_v}(\alpha_v)
    \end{align*}
    Since $\I_K$ is defined by restriced direct product, our definition is well-defined.
\end{definition}

\begin{definition}[Relative Artin Map]
    Consider a finite abelian extension $L/K$ of a global field $K$. The Relative Artin map is given by 
    \begin{align*}
        \theta_{L/K}: \I_K &\to \gal(L/K)\\
        (\alpha_v)_v&\mapsto \prod_{v}\theta_{L_w/K_v}(\alpha_v).
    \end{align*}
\end{definition}

\begin{theorem}[Artin Reciprocity Law]
    The relative Artin map of $L/K$ is surjective and with kernel $$\ker(\theta_{L/K}) = K^\times \cdot N_{L/K}(\mathbb{I}_L).$$
    It induces an isomorphism 
    \begin{align*}
         \I_K/(K^\times \cdot N_{L/K}(\mathbb{I}_L)) \simeq \gal(L/K).
    \end{align*}
    We can also write 
    \begin{align*}
        C_K/N_{L/K}(C_L) \simeq \gal(L/K).
    \end{align*}
\end{theorem}

Now we consider the "the functor of point" perspective in Class Field Theory.  Mainly, we interpret an element $a\in K$ as the representation of absolute galois group $G_K$.

To show that, we consider Kummer Theory. Let $K$ be a field contains $\mu_n$. Let $a$ be an arbitrary nonzero element of $K$.
We consider the spliting field of $x^n-a$.
In algebraically closed field $\bar{K}$, we must have the decomposition
\begin{align*}
    (x-\sqrt[n]{a})(x-\zeta_n\cdot \sqrt[n]{a})\cdots (x-\zeta_n^{n-1}\cdot \sqrt[n]{a})
\end{align*}
Let $\sigma$ be an arbitrary element of $G_K$, then we consider 
\begin{align*}
    \frac{\sigma(\sqrt[n]{a})}{\sqrt[n]{a}} = \zeta^{k}
\end{align*}
for some $k$. Actually, we use a type of polynomials $x^n-y$ induces the character
\begin{align*}
    K^\times \to \hom_{\text{grp}}(G_K,\mu_n).
\end{align*}

Actually, if we consider galois cohomology, then $G_K$ act trivially on $\mu_n$ since $\mu_n\subseteq K$.
In this sense we have 
\begin{align*}
    H^1(G_K,\mu_n) \simeq \hom_{\text{cont}}(G_K,\mu_n)
\end{align*}

Then kummer exact sequence 
\begin{align*}
    1\to \mu_n(K) \to K^\times \xrightarrow{(\cdot)^n} K^{\times} \to 1
\end{align*} 
induces a long exact sequence 
\begin{align*}
    1\to \mu_n(K) \to K^\times \xrightarrow{(\cdot)^n} K^{\times} \to H^1(G_K,\mu_n(K)) \to H^1(G_K,K^\times) \to \cdots
\end{align*}
Hilbert's 90 implies that $H^1(G_K,K^\times)=0$ then we have the following corollary.
\begin{corollary}[Kummer Isomorphism]
    Let $K$ be an arbitrary field contains $\mu_n$. Then we have an isomorphism 
    \begin{align*}
        K^\times/K^{\times n} \simeq H^1(G_K,\mu_n) \simeq \hom_{\text{cont}}(G_K,\mu_n). 
    \end{align*}
\end{corollary}

We have bijection 
\begin{center}
    \{Finite abelian extension $L/K$\} $\leftrightarrow$  \{Finite subgroups of $G_K^\vee$\}
\end{center}


Another $G_K$-module we usually consider in Class Field Theory is $\bar{K}^\times$.
Here, we must notice that $K$ is a local field.
So what the element of $K$ stand for in this sense? 
Let we consider $K$ acts on the Pontryagin dual group $G_{K}^\vee$, which defined by 
\begin{align*}
    a: G_K^\vee &\to \Q/\Z\\
    \chi&\mapsto \chi(\theta_K(a)).
\end{align*}
where $\theta_K$ means artin map.

Actually, it is the Tate-Nakayami duality. We first intepret $a$ as an element of $H^0(G_K,\bar{K}^\times)$ and $\chi$ as an element 
\begin{align*}
    H^1(G_K,\Q/\Z) \simeq G_K^\vee. 
\end{align*}

The exact sequence 
\begin{align*}
    0\to \Z \to \Q \to \Q/\Z \to 0
\end{align*}

We notice that $H^i(G_K,\Q)$ since $H^i(G,\Q)=0$ for $i>0$ and any finite group $G$.

Then know that 
\begin{align*}
    H^1(G_K,\Q/\Z) \simeq H^2(G_K,\Z).
\end{align*}

We consider the cup product 
\begin{align*}
    H^2(G_K,\Z) \cup H^0(G_K,\bar{K}^\times) \to  H^2(G_K,\Z\otimes_\Z \bar{K}^\times)
\end{align*}

Therefore we have 
\begin{align*}
    \delta(\chi) \cup a \in H^2(G_K,\bar{K}^\times)
\end{align*}

The Hasse invariant map tells 
\begin{align*}
    \text{inv}:H^2(G_K,\bar{K}^\times) \xrightarrow{\simeq} \Q/\Z.
\end{align*}





Now we turns to the global situation. Given an element $a\in \I_K$ and $\chi \in G_K^\vee$ we define pairing 
\begin{align*}
    \langle \chi,(a_v)_v \rangle:= \sum_{v} \text{inv}_v(\delta(\chi_v)\cup a_v) \in \Q/\Z
\end{align*}

We also call the second cohomology group as Brauer group $\br(K) = H^2(G_K,\bar{K}^\times)$. 
An important exact sequence to give the well-definedness of this pairing is following theorem.

\begin{theorem}[Hasse exact sequence]
    Let we consider global field $K$. Then we have a exact sequence of Brauer group 
    \begin{align*}
        0\to \br(K) \to \bigoplus_{v}\br(K_v) \xrightarrow{\sum_v \text{inv}} \Q/\Z \to 0
    \end{align*}
\end{theorem}

The exact sequence implies that if $(a_v)_v$ is principle i.e. $(a_v)_v \in K^\times$, we then have 
\begin{align*}
    \langle \chi,(a_v)_v \rangle =0.
\end{align*}

Then we obtain that the pairing of global field
\begin{align*}
    C_K \times H^1(G_K,\Q/\Z) \to \Q/\Z. 
\end{align*}





Now let we return to Kummer theorem again. Let $K$ be a field containing $\mu_n$. We can interpret 
$\mu_n$ as torsion submodule of $\bar{K}^\times$.



In this case, the Hilbert symbol over $K_v$ is defined by 
\begin{align*}
    (\chi_a,b)_v &\mapsto \frac{\theta_b(\sqrt[n]{a})}{\sqrt[n]{a}}
\end{align*}
where $\chi_a\in K_v^\times/(K_v^{\times n})$ is Kummer character given by Kummer exact sequence
and $b$ is an element of $K_v$. $\theta_b$ is $\theta(b)$ the image of local artin map.

The global case of Hilbert reciprocity law is 
\begin{align*}
    \prod_v(a,b)_v = 1
\end{align*}

Now we give the definition of local artin map over $\Q_\p$. Consider the fintie abelian extension $K/\Q_p$. Let $x=up^m\in\Q_p^\times$.
The artin map is given by
\begin{align*}
    \theta_{\Q_p}(p) = \text{Frob}_p.
\end{align*}
and 
\begin{align*}
    \theta_{\Q_p}(u)(\zeta_{p^r}) = \zeta_{p^r}^{u \bmod p^r}
\end{align*}


The calculation of quadratic Hilbert symbol. 
Let $p$ be odd prime number.
Consider $\Q_p$ and $a=p^\alpha u, b = p^\beta v$. Then the Hilbert sysmbol is given by 
\begin{align*}
    (a,b)_p = (-1)^{\alpha\beta\frac{p-1}{2}} \legendre{\bar{u}}{p}^\beta \legendre{\bar{v}}{p}^\alpha 
\end{align*}
where $\bar{u},\bar{v}\in \F_p$.
The legendre symbol is defined by 
\begin{align*}
    \legendre{a}{p} = a^{\frac{p-1}{2}}\bmod p
\end{align*}

We also have
\begin{align*}
    \legendre{2}{p} = (-1)^{\frac{p^2-1}{2}}.
\end{align*} 

The reprocity law 
\begin{align*}
    \legendre{q}{p}\legendre{p}{q} = (-1)^{\frac{p-1}{2}\frac{q-1}{2}}.
\end{align*}

Also we should know 
\begin{align*}
    (a,b)_{\infty} = -1 \text{ if }a,b<0
\end{align*}


The Hilbert symbol has good properties: 
\begin{enumerate}
    \item[bilinear] $(aa',b) = (a,b)(a',b)$
    \item[skew-sysmetric] $(a,b)(b,a)=1$
    \item[non-degenerated] $(a,b)=1$ for all $b$ iff. $a\in K^{\times n}$  
\end{enumerate}


\section*{Problems}
\prob  Let $D$ be a square-free integer, $D\neq 0,1$. For a prime number $l$, prove that if $l\mid D$, then $l$ is ramified in $\Q(\sqrt{D})$.

Since $D$ be a square-free integer and $l\mid D$, then we must have $v(D)=1$. Then we have $v(\sqrt{D})=1/2$ implies it is ramified.

\prob Analysis Cyclotomic extension $\Q(\zeta_n)$.

The cyclotomic polynomial are given by 
\begin{align*}
    \Phi(x) = \sum_{k=1,(n,k)=1}(x-\zeta_n^k).
\end{align*}
Therefore $[\Q(\zeta_n):\Q]=\varphi(n)$. The Euler function $\varphi(p^k)=p^k-p^{k-1}$. 
The galois group of this extension is given by  $(\Z/n\Z)^\times$. We need to notice that $|(\Z/p^k\Z)^\times|=\varphi(p^k)$.

\prob Every quadratic extension over $\Q$ must have the form $\Q(\sqrt{D})$. It is Galois and its roots of unity only have three types.

Clealy, Consider $\Q(\alpha)$ where $\alpha$ with minimal polynomial $f(x)$. 
According to the Vieta's formulas, we must have $\beta = \alpha^{-1}c/a$. It is the split field of $f(x)$ and hence it is galois.

The galois group must have order two, it should be $\Z/2\Z$.

Let $D$ be the the square-free part of the square of determinant $\sqrt{\Delta}$ of $f(x)$, then we can check that $\Q(\alpha)=\Q(\sqrt{D})$.

Suppose that $\Q(\zeta_{p^m})\subseteq \Q(\alpha)$. Since $[\Q(\zeta_{p^m}):\Q] = \varphi(p^m) = p^{m-1}(p-1)$. Then inequality 
\begin{align*}
    p^{m-1}(p-1)\le 2
\end{align*}
tell us it only can be the case: 
\begin{enumerate}
    \item $p=3,m=1$.
    \item $p=2,m=1$.
    \item $p=2,m=2$.
\end{enumerate}
It corresponds to the the roots of unity $W_k$
\begin{enumerate}
    \item $\langle -1,\omega,\omega^2 \rangle$
    \item $\langle -1 \rangle$
    \item $\langle -1,i \rangle$
\end{enumerate}
Clearly $D>0$ then we have $W_k = \langle -1\rangle$. If $D=-3$, then we find that $\Q(\frac{\sqrt{-3}+1}{2})=\Q(\zeta_3)$. 
If $D=-1$, it must be $\Q(i)$. And others situation must have root of unity $\langle -1\rangle$.

\prob The roots of unity over $\F_{p^t}$. 

Since every element $x\in \F_{p^t}$ we have $x^{p^t-1}=1.$ Then $x^n=1$ and $(n,p)=1$ iff. $n|p^t-1$.
If $p\mid n$, then we find that $x^{kp^s}-1=(x^k-1)^{p^s}=0$.

\prob Kronecker-Weber Theorem state that every Abel number field is a subfield of a cyclotomic number field. Find this field for quadratic extension $\Q(\sqrt{D})$.

Let we consider the determinant $\Delta$ of $f(x)$ which is the minimal polynomial of $\sqrt{D}$.
Then consider $\Q(\zeta_{|\Delta|})$.



\prob Classical Group in Galois Theory.

There are several classical group we need to know.
\begin{enumerate}
    \item Symmetric group $S_n$
    \item Alternating Group $A_n$
    \item Cyclic Groups $\Z/n\Z$
    \item Dihedral Groups $D_n = \Z/n\Z \rtimes \Z/2\Z.$
    \item Klein Four Group $V_4 = (\Z/2\Z)^2$
    \item Frobenius Groups $\text{AGL}(1,p)= \Z/p\Z \rtimes (\Z/p\Z)^\times.$
\end{enumerate}



\prob Discriminant of $x^n+ax+b$.

We use the fact that $\Delta(f)=(-1)^{n(n-1)/2}\text{Res}(f,f')$. And 
$$\text{Res}(f,f')=(-1)^{n-1}(n-1)^{n-1}a^n+n^nb^{n-1}.$$

\prob Consider $\Q(\alpha)$ and with $f(x)=x^3-x+1$. Calculate the norm of $\alpha+2$.

We compute the discriminant of $f$ by 
\begin{align*}
    \Delta(f) = (-1)\text{Res}(f,f') =-23. 
\end{align*}
Let $g(x)=x+2$, then we have 
\begin{align*}
    \N_{L/K}(\alpha+2) =  \text{Res}(f,g).
\end{align*}

Also we can find the spliting field of $f(x)$ is $\Q(\alpha,\sqrt{23})$. 
Then $\sqrt{23}\cdot \ok $ lying over $23\cdot \Q$. We next compute the 
\begin{align*}
    \N_{L/K}(\alpha) = \text{Res}(f,x) = -1.
\end{align*} 

\prob Verify the integral closure of $\Z[\alpha]$. 

Since $\Delta(f) = -23$ is square-free, it means that $\Z[\alpha]$ is integral. 

\prob Let $K(\sqrt{D})$ with $D$ is square-free. Prove that $\ok=\Z[\sqrt{D}]$ if $D\equiv 2,3\bmod 4$ and $\ok=\Z[\frac{1+\sqrt{D}}{2}]$ if $D\equiv 1\bmod 4$. 

Consider the discriminant of an order $\Z[\sqrt{D}]$ is given by 
\begin{align*}
    \d(\Z[\sqrt{D}]) = 4D
\end{align*}
The only value of $[\ok:\Z[\sqrt{D}]]$ is 1 or 2.
Suppose that $D\equiv 2,3\bmod 4$ with $[\ok:\Z[\sqrt{D}]]=2$. Then we have an element
\begin{align*}
    y = \frac{a+b\sqrt{D}}{2}
\end{align*}
is intergral. We have a minimal polynomial
\begin{align*}
    f(x) = (x-y)(x-\sigma(y)) = x^2-ax+\frac{a^2-b^2 D}{4}
\end{align*}
It must have $\frac{a^2-bD}{4}$ be an integer. It is impossible.

\prob Find the Galois group of $\Q(\alpha,\sqrt{-23})/\Q$.

Clearly it permutes the roots of $f$. Since $f(x)$ is irreducible then it must be transitive.
The transitive subgroup of $S_3$ are $A_3$ or $S_3$. It can not be $A_3$ since $[\Q[\alpha,\sqrt{-23}]:\Q]=6$.
Also, the determinant $d=-23$ implies it admits two complex roots. consider the conjugate action, it is a odd permutation.
Therefore, the galois group cannot be $A_3$.





\prob Analysis the integrality of $M=\Z[\alpha,\frac{1+\sqrt{-23}}{2}]$.

We consider the field extension $\Q(\alpha,\sqrt{-23})/\Q(\alpha)$ with minimal polynomial $g(x)=x^2-x+6$.
We consdier the determinant of $g$ is given by 
\begin{align*}
    \Delta = -23
\end{align*}
Therefore the determinant of $M$ is given by calculate the determinant of $\{\alpha,\alpha^2,\alpha^3,\omega\cdot \alpha,\dots\}$
where we let $\omega = \frac{1+\sqrt{-23}}{2}$. Then we have 
\begin{align*}
    \Delta_{M} = (-23)^{2} \cdot (-23)^{3} = -23^5.
\end{align*}

Let $L=\Q(\alpha,\sqrt{-23})$, $K_1=\Q(\sqrt{-23})$, $K_2=\Q(\alpha)$.
Now we compute the determinant of field extension. I claim that the field extension $\Q(\alpha,\sqrt{-23})/\Q(\sqrt{-23})$
is unramified. Then $\D(L/K_1)=\ol$ and thus $\d(L/K_1)=\o_{K_1}$. Consider the tower of Different 
\begin{align*}
    \D(L/\Q) = \D(L/K_1)\cdot \D(K_1/\Q)
\end{align*}
and act on $N_{L/\Q}$ on both side.
We then have 
\begin{align*}
    \d(L/\Q)=N_{K_1/\Q}(\d(L/K_1))\cdot \d(K_1/\Q)^{[L:K_1]}.
\end{align*}
And we have 
\begin{align*}
    \d(L/\Q)= (-23)^3
\end{align*}

Now we prove our claim.  

First, you can check $K_1/\Q$ and $K_2/\Q$ are only ramified at $23$. Therefore $L/Q$ only ramified at $23$.




Then you check $\Q_{23}(\alpha,\sqrt{-23})/\Q_{23}$ has degree $2$. It implies that ramification index cannot larger than 2.
Therefore $L/K_1$ is unramified.

\prob Analysis the decomposition of $(23)$ from the tower $\Q\to K_1\to L$.

Consider $\Q_{23}(\sqrt{-23})/\Q_{23}$ with a minimal polynomial $g(x)$. The newton polygon of $g(x)$ tells its ramification index is 2.
And since $K_1/\Q$ is quadratic extension, it must be totally ramified at $(23)$ over $K_1$. Now suppose that 
\begin{align*}
    23\cdot K_1 = \p^2.
\end{align*}
We then consider the $K_1(\alpha)_\p/(K_1)_\p$ with a minimal polynomial $f(x)$. 
Consider the polynomial over residue field 
\begin{align*}
    x^3-x+1 \mod \p.
\end{align*}
Since $f(3)\equiv 0\mod \p$ and $f'(3) = 26\not\equiv 0\mod\p $. We obtain that $x=3$ be the simple root of $f(x)$ according to Hensel's lemma.
According to the symmetric of galois extension we then have 
\begin{align*}
    23\cdot \ol = (\P_1\P_2\P_3)^2
\end{align*}

\prob Analysis the decomposition of $(23)$ by using $L\otimes_{\Q}\Q_{23}$.

Basically, we use the fact that 
\begin{align*}
    L\otimes_{\Q}\Q_{23}  = (K_1\otimes_\Q \Q_{23})\otimes_{\Q_{23}}(K_2\otimes_\Q \Q_{23})
\end{align*}
Analysis $K_1/\Q$ we now that $g(x)$ split over residue field. Then we obtain that 
\begin{align*}
    K_1\otimes_\Q \Q_{23}  = \Q_{23}(\sqrt{-23}).
\end{align*}

Next we consider $K_2/\Q$ since 
\begin{align*}
    f(x)\equiv (x-3)(x-10)^2 \bmod 23
\end{align*}

Let $x=y+10$, we find that 
\begin{align*}
    f(y)  = x^3+30x^2+299x+991
\end{align*}
with Newton polygon
\begin{align*}
    (0,1) \to (0,1) \to (0,0) \to (0,0)
\end{align*}
It menas that $K_2/\Q$ must ramified, then we obtain that 
\begin{align*}
    K_2\otimes_\Q \Q_{23} \simeq \Q_{23} \times E_2 
\end{align*}
Where $E_2$ denotes an totally ramified extension of $\Q_{23}$ with $e=2,f=1$.
According to the calssification of local field extension, we claim it is equivalent to $\Q_{23}(\sqrt{-23})$.
Therefore we then have 
\begin{align*}
    L\otimes_{\Q}\Q_{23} &= \Q_{23}(\sqrt{-23})\otimes_{\Q_{23}} (\Q_{23}\times \Q_{23}(\sqrt{-23}))\\
    &=\Q_{23}(\sqrt{-23}) \times \Q_{23}(\sqrt{-23}) \times \Q_{23}(\sqrt{-23}).
\end{align*} 

\prob Analysis the decomposition group and inerita group of $(23)$.

We have 
\begin{align*}
    D_\P = \gal(\Q_{23}(\sqrt{-23})/\Q_{23}) = \Z/2\Z
\end{align*}
and exact sequence 
\begin{align*}
    0\to I_\P \to D_\P \to \gal(\kappa(\P)/\F_{23}) \to 0
\end{align*}
Since $\kappa(\P)/\F_{23}$ is trivial then we have $I_\P=D_\P=\Z/2\Z$.



\prob Analysis the decomposition of $(2)$.

We consider $L\otimes_{\Q}\Q_{2}$. Since $g(x)$ split over $\F_2$, it menas that 
\begin{align*}
    K_1\otimes_\Q \Q_2 = \Q_2\times \Q_2.
\end{align*}
Since $x^3-x+1$ has not root. It means that the inertia degrre $f=3$. Therefore we have 
\begin{align*}
    K_2 \otimes_\Q \Q_2 = \Q_{2^3}.
\end{align*}
Then we have 
\begin{align*}
    L\otimes_\Q \Q_2 = \Q_{2^3} \times \Q_{2^3}.
\end{align*}

\prob Calculate the frobenius element corresponding to (2).

We find it over extension $\Q_{2^3}/\Q_{2}.$ Consider its residue field is $\F_{2^3}$. 
The frobenius map $x\mapsto x^2$ has order 3 in this residue field. 
It menas $\text{Frob}_\P$ in $\text{Gal}(L/\Q)$ must have order 3. The only case is (123).

\prob Analysis the decomposition of $(59)$ over $L$.

Similarly, we again Consider $\Q_{59}(\alpha,\sqrt{-23})/\Q_{59}$. Consider that 
\begin{align*}
    f(x) \equiv (x-4)(x-13)(x-42)\mod 59  
\end{align*}
and we have 
\begin{align*}
    g(x) = (x-3)(x+3) \mod 59.
\end{align*}
It means that $f(\Q_{59}(\alpha)/\Q_{59})=f(\Q_{59}(\sqrt{-23})/\Q_{59})=1$. 
Consider that it is unramified, then we obtain it is totally split.

\prob The extension $\Q_l(\zeta_p)/\Q_l$ is unramified for $l\neq p$.

Consider that $\zeta_p^{p}=1$, then we have $v(\zeta_p^p)=0$, which menas that the value group is not change.

\prob The extension $\Q_p(\zeta_p)/\Q_p$ is totally ramified.

Since $x^p-1\equiv (x-1)^p\bmod p$, it means that $f=1$.

Hence we consider that 
\begin{align*}
    x^{p-1} + \binom{p}{1}x^{p-1}+\binom{p}{2}x^{p-2}+\dots+p
\end{align*}
It is irreducible over $\Q_p$ according to Dumas's criterion. It implies that the extension of local field is totally ramified.


\prob Let $K=\Q(\sqrt[3]{m})$ with $m=ab^2$. Let $\alpha=\sqrt[3]{ab^2}$ and $\beta=\sqrt[3]{a^2b}$. Calculate the determinant of field $K$.

We use a fact that $K/\Q$ ramified over $p$ iff. $p|d_K$. Consider $K=\Q(\alpha)=\Q(\beta)$ with minimal polynomials $f(x)= x^3-ab^2$ and $g(x)=x^3-a^2b$.
Newtow polygon tells every prime number $p$ such that $p|ab$ is totally ramified.
Therefore $d_K$ must contains factors $a,b$. We consider the determinant of an order 
\begin{align*}
    d(1,\alpha,\beta) = -27a^2b^2
\end{align*}
Since $a,b$ are square free and the different between the discriminant of an order and field is squre factor. Therefore, we claim there are two possibility 
\begin{align*}
    d_K = -27a^2b^2\text{ or }-3a^2b^2.
\end{align*}

When $3|a$ then  3 is totally ramified. One fact that we have is 
\begin{align*}
    3\nmid [\ok:\Z[\alpha]].
\end{align*}
Suppose that $(3) =\p^3$ and $v_\p(\alpha)=k$. Then we have 
\begin{align*}
    3v_\p(\alpha) = v_\p(a)=3.
\end{align*}
Suppose that $[\ok:\Z[\alpha]]=3g$, then we have 
$$(3g)^{-1}\Z[\alpha]\subseteq \ok$$  
which is impossible. 

For same reason, if $3|b$, we also have 
\begin{align*}
    3\nmid [\ok:\Z[\beta]].
\end{align*}

Consider that 
\begin{align*}
    [\ok:\Z[\alpha,\beta]] | [[\ok:\Z[\alpha]]] 
\end{align*}
or 
\begin{align*}
    [\ok:\Z[\alpha,\beta]] | [[\ok:\Z[\beta]]].
\end{align*}
we have 
\begin{align*}
    3\nmid [\ok:\Z[\alpha,\beta]]. 
\end{align*}
Since $[\ok:\Z[\alpha,\beta]]$ must equal to 1 or 3 and 3 is impossible.
Then we find that if $3|ab$ then $d_K = -27a^2b^2$.

\prob Prove that $\Q(\zeta_n+\zeta_n^{-1})$ is the maximal real subfield of $\Q(\zeta_n)$.

Consdier that $\zeta_n$ is the locus of 
\begin{align*}
    x^2-(\zeta_n+\zeta_n^{-1})x+1 
\end{align*}

\prob The decomposition of cyclotomic polynomial
$$\Phi_n(x) = \prod_{d \mid n} (x^{n/d} - 1)^{\mu(d)}$$
an examples:
$x^6 - 1 = \Phi_1(x)\Phi_2(x)\Phi_3(x)\Phi_6(x).$

\prob Give the relation between the number of complex embedding $r_2$ with determinant of $f$.

Let $\Delta$ be the determinant then we have
\begin{align*}
    \Delta = \prod(\alpha_i-\alpha_j)^2
\end{align*}
We have $(\alpha_i-\bar{\alpha_i})<0$, therefore we then have 
\begin{align*}
    \text{sgn}(\Delta) = (-1)^{r_2}
\end{align*}



\prob Calculate the class group of $\Q(\sqrt{-5})$.

Since $-5\equiv 2\bmod 4$, we have $d_K = 4D$ and 
\begin{align*}
    \ok = \Z[\sqrt{-5}].
\end{align*}
It has $r_1=0$ and $r_2=2$. 
We calculate the Minkowski bound 
$$M_K = \frac{n!}{n^n} \left(\frac{4}{\pi}\right)^{r_2} \sqrt{|d_K|} \approx 2.84$$

Therefore, we just need to consider $(2)$. According to Dedekind-Kummer theorem, the decomposition of 
\begin{align*}
    x^2+5 \equiv (x+1)^2 \bmod 2
\end{align*}
implies that $(2)$ is totally ramified 
\begin{align*}
    (2) = \p^2
\end{align*}
Where $\p=(2,1+\sqrt{-5})$. Therefore $\Cl(K)$ is generated by $[\p]$. We just need to show that $\p$
is not principle. Suppose that 
\begin{align*}
    (a+b\sqrt{-5}) = \p
\end{align*}
Act on norm on both side we have 
\begin{align*}
    2= a^2+5b^2.
\end{align*}
It has no integer solution. Therefore we have $\Cl(K)=\Z/2\Z$. 


\prob Suppose that $N(\p)=l$ where $\p$ is a prime ideal and $l$ is a prime number. Then if $N(\alpha) = l$, then we have 
\begin{align*}
    (\alpha) = \p.
\end{align*}


\prob Consider the transitive subgroup of $S_4$.

It only contains 

\prob Consider the Kummer extension of $\Q_p$

\prob Find the fundamental 

\section*{Class Field Theory}
\textbf{Idele class group}

The Idele group is defined by 
$$\mathbb{I}_L = \prod_{v \in V} \nolimits' L_v^\times = \{ (\alpha_v)_{v \in V} \mid \alpha_v \in K_v^\times, \text{all but finitely many } v, \alpha_v \in U_v \}$$

If we consider the field extension $L/K$, then we have 
$$\mathbb{I}_L = \prod_{v \in V_K} \left( \prod_{w|v} L_w^\times \right)$$

Idele class group is defined by $\I_L/L^\times$.

There is a exact sequence 
\begin{align*}
    1\to L^{\times} \to \I_L \to C_L \to 1.
\end{align*}

\textbf{invariant functor}

Let $G_K$ be the absolute galois group. Invariant functor $(\cdot)^{G_K}$ can be written by 
\begin{align*}
    (M)^{G_K} = \hom_{\Z[G_K]}(\Z,M).
\end{align*}
for arbitrary $G_K$-module $M$.


\textbf{Kummer exact sequence}

Let $K$ be a field such that $\char(K)\nmid n$. We have Kummer exact sequence 
\begin{align*}
    1\to \mu_n(K) \to \bar{K}^\times \xrightarrow{(\cdot)^n} \bar{K}^{\times} \to 1
\end{align*} 
and 
\begin{align*}
    1\to \mu_n(K) \to \o_{\bar{K}}^\times \xrightarrow{(\cdot)^n} \o_{\bar{K}}^{\times} \to 1.
\end{align*} 

It induces long exact sequences given by 
\begin{align*}
    1\to \mu_n(K) \to \bar{K}^\times \xrightarrow{(\cdot)^n} \bar{K}^{\times} \to H^1(G_K,\mu_n(K)) \to H^1(G_K,\bar{K}^\times) \to \cdots
\end{align*}
and 
\begin{align*}
    1\to \mu_n(K) \to \o_{\bar{K}}^\times \xrightarrow{(\cdot)^n} \o_{\bar{K}}^{\times}  \to H^1(G_K,\mu_n(K)) \to H^1(G_K, \o_{\bar{K}}^\times) \to \cdots
\end{align*}

\textbf{Hilbert's 90 theorem}

We have Hilbert's 90 theorem.
\begin{enumerate}
    \item $H^1(G_K,\bar{K}^\times)=0$.
    \item $L/K$ be the finite galois extension over a local field $K$. Then we have $H^1(G, L^\times) = 0.$
    \item Addtivit form above. we have $H^i(G, L) = 0$ for all $i\ge 1$.
    \item If $L/K$ is the fintie galois extension over global field. we have $H^1(G, L^\times) = 0.$
    \item We have $H^1(G, \I_L) = 0$ and $H^1(G, C_L) = 0$.
\end{enumerate}


\textbf{Shapiro's Lemma}

Shapiro's lemma claim that 

$$H^i(G, \mathrm{Ind}_H^G(M)) \cong H^i(H, M) \quad (\forall i \ge 0)$$

therefore we have 
$$H^i(G, \I_L) \cong \bigoplus_{v} H^i(D_\P, L_w^\times) \quad (\forall i \ge 0)$$

\textbf{The dimension of cohomology}

Consider $K$ is a local nonarchimedean field with finite $G_K$-module $M$.
Then 
\begin{align*}
    H^i(G_K,M) = 0
\end{align*}
for $i\ge 3$.

\textbf{The meaning of cohomology}

The zero order cohomology
\begin{align*}
    H^0(G_K,M) = M^{G_K}
\end{align*}
means the element of $M$ which is contained over base field.


\textbf{Tate Duality}

We consider local field $K$. 
\begin{align*}
    \mu_n = \{\zeta\in\bar{K}^\times\mid \zeta^n=1\}
\end{align*}
Let $\mu_\infty$ be the inductive limit of $\mu_n$.


Let $M$ be a finite $G_K$-module. Define Cartier duality by
\begin{align*}
    M^\vee = \ihom_{\Z}(M,\mu_{\infty})
\end{align*}

For $f\in M^\vee$, we have $\sigma \cdot f= \sigma f \sigma^{-1}$.
As a set it is equal to $\hom_{\Z}(M,\mu_{\infty}).$


\textbf{Hilbert Symbol and Artin Reciprocity Law}

The Hilbert Symbol and artin Reciprocity law are two essential and basic concept of Class Field Theory.




Consider local field $K$ with $\mu_n\subseteq K$. The Hilbert symbol is defined by 
\begin{align*}
    (\cdot,\cdot)_K: (K^\times/K^{\times n}) \times (K^\times/K^{\times n}) &\to \mu_n\\
    (a,b)_K &\mapsto \frac{\sigma_b(\sqrt[n]{a})}{\sqrt[n]{a}}
\end{align*}
where 
\begin{align*}
    \sigma_b:K^\times \to G_K^{\ab}
\end{align*}
is the Artin map. 




The meaning of Hilbert symbol is quite simple. That is 
\begin{align*}
    (a,b)_K=1\Longleftrightarrow a\in N_{L/K}(L^\times)\Longleftrightarrow  \text{The equation }x^n-a=0\text{ has solution over }L
\end{align*}
where $L=K(\sqrt[n]{b})$


local/global class field, tate duality, Hilbert class, reprocity, gal cohomology, kummer exact sequence
Herbrand

The formula 

\prob Prove that $x^2+5=y^3$ does not has a integer solution.

\prob Consider the quadratic Hilbert symbol, prove that $(-1,-1)_2 = -1$ and $(2,5)_2 = -1$.

Suppose that $(2,5)=1$. It means the norm function 
\begin{align*}
    a^2-2b^2= 5
\end{align*}
has a solution over $\Q_2$. First $a,b\in \Z_2$, if not we obtain that $v_2(5)<0$. 
Therefore we can consider mod 8. The only quadratic element mod 8 are 1 or 4. The only possible mod 8 of LHS are 0,1,2,4,6,7. 
The same as $(-1,-1)_2$.


\prob Consider the decomposition of $\Q_2^\times$ and $\Q_2^\times/\Q_2^{\times 2}$. Deduce the Hilbert symbol for $\Q_2$.

We has 
\begin{align*}
    \Q_2^\times\simeq \Z\times \Z_2^\times \simeq \Z\times (1+4\Z_2)\times \mu_2.
\end{align*}

Therefore we have 
\begin{align*}
    \Q_2^\times/\Q_2^{\times 2} = \langle -1,3,5 \rangle \simeq (\Z/2\Z)^3.
\end{align*}


\prob Let \(L=\mathbf Q(\sqrt 2)\). Determine whether the norm equation
$N_{L/\mathbf Q}(z)=3$
has a solution \(z\in L^\times\). Equivalently, decide whether
$x^2-2y^2=3$
has a solution in \(\mathbf Q\). Use local Hilbert symbols.

Since \(L/\mathbf Q\) is cyclic, the Hasse norm theorem says
\[
3\in N_{L/\mathbf Q}(L^\times)
\iff
3\in N_{L_v/\mathbf Q_v}(L_v^\times)
\quad\text{for all places }v.
\]
For the quadratic extension \(L=\mathbf Q(\sqrt2)\), the local norm condition is
\[
3\in N_{\mathbf Q_v(\sqrt2)/\mathbf Q_v}
\bigl(\mathbf Q_v(\sqrt2)^\times\bigr)
\iff
(2,3)_v=1.
\]

We compute \((2,3)_v\). For odd \(p\), write
\[
a=p^\alpha u,\qquad b=p^\beta v,
\]
with \(u,v\in\mathbf Z_p^\times\). Then
\[
(a,b)_p
=
(-1)^{\alpha\beta\frac{p-1}{2}}
\left(\frac{\bar u}{p}\right)^\beta
\left(\frac{\bar v}{p}\right)^\alpha.
\]

If \(p\neq 2,3\), then \(2,3\in\mathbf Z_p^\times\), so
\[
(2,3)_p=1.
\]

For \(p=3\),
\[
2=3^0\cdot 2,\qquad 3=3^1\cdot 1,
\]
hence
\[
(2,3)_3=\left(\frac{2}{3}\right)=-1.
\]

For \(p=2\), use the formula
\[
(a,b)_2
=
(-1)^{
\epsilon(u)\epsilon(v)
+\alpha\omega(v)
+\beta\omega(u)
},
\]
where
\[
\epsilon(u)=\frac{u-1}{2}\pmod 2,
\qquad
\omega(u)=\frac{u^2-1}{8}\pmod 2.
\]
Since
\[
2=2^1\cdot 1,\qquad 3=2^0\cdot 3,
\]
we get
\[
(2,3)_2
=
(-1)^{\omega(3)}
=
(-1)^{(9-1)/8}
=
-1.
\]

At the real place,
\[
(2,3)_\infty=1
\]
because \(2>0\) and \(3>0\).

Therefore
\[
(2,3)_2=(2,3)_3=-1,
\qquad
(2,3)_v=1\quad\text{for }v\neq 2,3.
\]
In particular,
\[
(2,3)_2\neq 1,
\]
so \(3\) is not a local norm from \(\mathbf Q_2(\sqrt2)\). Hence it is not a global norm.

Thus
\[
\boxed{
N_{\mathbf Q(\sqrt2)/\mathbf Q}(z)=3
\text{ has no solution in } \mathbf Q(\sqrt2)^\times.
}
\]

Equivalently,
\[
\boxed{
x^2-2y^2=3
\text{ has no solution in } \mathbf Q.
}
\]

Finally, Hilbert reciprocity is still satisfied:
\[
\prod_v(2,3)_v
=
(2,3)_2(2,3)_3
=
(-1)(-1)=1.
\]


\np Let \(K=\mathbf Q_3\), and let
\[
L=K(\sqrt 2).
\]
Let
\[
\chi\in H^1(G_K,\mathbf Q/\mathbf Z)
=
\operatorname{Hom}_{\mathrm{cont}}(G_K,\mathbf Q/\mathbf Z)
\]
be the quadratic character corresponding to \(L/K\), normalized so that the
nontrivial element has value \(1/2\in \mathbf Q/\mathbf Z\).

Using the cohomological Artin reciprocity pairing
\[
H^1(G_K,\mathbf Q/\mathbf Z)\times K^\times
\longrightarrow \mathbf Q/\mathbf Z,
\]
\[
(\chi,b)\longmapsto
\operatorname{inv}_K\bigl(\delta(\chi)\cup b\bigr),
\]
where
\[
\delta(\chi)\in H^2(G_K,\mathbf Z)
\]
comes from
\[
0\to \mathbf Z\to \mathbf Q\to \mathbf Q/\mathbf Z\to 0,
\]
and
\[
\delta(\chi)\cup b\in
H^2(G_K,\bar K^\times)=\operatorname{Br}(K),
\]
compute
\[
\operatorname{inv}_K\bigl(\delta(\chi)\cup 3\bigr).
\]
Then compare your answer with
\[
\chi(\operatorname{Art}_K(3)).
\]

\[
\textbf{Solution.}
\]
Since \(2\) is not a square modulo \(3\), the extension
\[
L=\mathbf Q_3(\sqrt 2)
\]
is the unramified quadratic extension of \(\mathbf Q_3\).

By local Artin reciprocity, if we choose the convention
\[
\operatorname{Art}_K(3)=\operatorname{Frob}_3,
\]
then \(\operatorname{Art}_K(3)\) is the nontrivial element of
\[
\operatorname{Gal}(L/K)\cong \mathbf Z/2\mathbf Z.
\]
Therefore
\[
\chi(\operatorname{Art}_K(3))=\frac12.
\]

Now compute the cohomological side. The class
\[
\delta(\chi)\cup 3
\in H^2(G_K,\bar K^\times)
=
\operatorname{Br}(K)
\]
is the Brauer class corresponding to the quadratic Hilbert symbol
\[
(2,3)_3.
\]
For odd \(p\), if
\[
a=p^\alpha u,\qquad b=p^\beta v,
\]
with \(u,v\in \mathbf Z_p^\times\), then
\[
(a,b)_p
=
(-1)^{\alpha\beta\frac{p-1}{2}}
\left(\frac{\bar u}{p}\right)^\beta
\left(\frac{\bar v}{p}\right)^\alpha.
\]
Here
\[
2=3^0\cdot 2,\qquad 3=3^1\cdot 1.
\]
Hence
\[
(2,3)_3
=
\left(\frac{2}{3}\right)
=
-1.
\]
The value \(-1\in \mu_2\) corresponds to
\[
\frac12\in \frac12\mathbf Z/\mathbf Z
\subset \mathbf Q/\mathbf Z.
\]
Therefore
\[
\operatorname{inv}_K\bigl(\delta(\chi)\cup 3\bigr)
=
\frac12.
\]

Thus
\[
\boxed{
\operatorname{inv}_K\bigl(\delta(\chi)\cup 3\bigr)
=
\chi(\operatorname{Art}_K(3))
=
\frac12.
}
\]

This verifies the cohomological form of local Artin reciprocity in this example:
\[
\boxed{
\operatorname{inv}_K(\delta(\chi)\cup b)
=
\chi(\operatorname{Art}_K(b)).
}
\]


\[
\textbf{Problem.}
\]
Let
\[
L=\mathbf Q(\zeta_7)^+
\]
be the maximal real subfield of \(\mathbf Q(\zeta_7)\). Then
\[
[L:\mathbf Q]=3
\]
and
\[
\operatorname{Gal}(L/\mathbf Q)\cong \mathbf Z/3\mathbf Z.
\]

This extension is not a Kummer extension over \(\mathbf Q\), since
\[
\mu_3\not\subset \mathbf Q.
\]

\[
\textbf{(1)}
\]
Use global class field theory to compute
\[
C_{\mathbf Q}/N_{L/\mathbf Q}C_L.
\]

\[
\textbf{(2)}
\]
Interpret this quotient using Tate cohomology.

\[
\textbf{(3)}
\]
Determine the Artin symbols of the primes \(2\) and \(13\), and decide whether
\[
2,\ 13\in N_{L/\mathbf Q}(L^\times).
\]

\[
\textbf{Solution.}
\]

Since
\[
L=\mathbf Q(\zeta_7)^+
\]
is the real subfield of the cyclotomic field \(\mathbf Q(\zeta_7)\), we have
\[
\operatorname{Gal}(L/\mathbf Q)
\cong
(\mathbf Z/7\mathbf Z)^\times/\{\pm1\}.
\]
But
\[
(\mathbf Z/7\mathbf Z)^\times
=
\{1,2,3,4,5,6\}
\cong \mathbf Z/6\mathbf Z,
\]
so
\[
(\mathbf Z/7\mathbf Z)^\times/\{\pm1\}
\cong \mathbf Z/3\mathbf Z.
\]

By global class field theory, the Artin reciprocity map gives an isomorphism
\[
C_{\mathbf Q}/N_{L/\mathbf Q}C_L
\xrightarrow{\sim}
\operatorname{Gal}(L/\mathbf Q).
\]
Therefore
\[
\boxed{
C_{\mathbf Q}/N_{L/\mathbf Q}C_L
\cong
\mathbf Z/3\mathbf Z.
}
\]

Now let
\[
G=\operatorname{Gal}(L/\mathbf Q).
\]
Tate cohomology gives
\[
\widehat H^0(G,C_L)
=
C_{\mathbf Q}/N_{L/\mathbf Q}C_L.
\]
The fundamental class
\[
u_{L/\mathbf Q}\in H^2(G,C_L)
\]
induces, by Tate--Nakayama duality, an isomorphism
\[
\widehat H^{-2}(G,\mathbf Z)
\xrightarrow{\;\cup u_{L/\mathbf Q}\;}
\widehat H^0(G,C_L).
\]
But
\[
\widehat H^{-2}(G,\mathbf Z)
\cong
H_1(G,\mathbf Z)
\cong
G^{\mathrm{ab}}.
\]
Since \(G\) is already abelian,
\[
G^{\mathrm{ab}}=G.
\]
Hence
\[
\widehat H^0(G,C_L)
\cong
G.
\]
This recovers the class field theory isomorphism
\[
C_{\mathbf Q}/N_{L/\mathbf Q}C_L
\cong
\operatorname{Gal}(L/\mathbf Q).
\]

Now compute Frobenius elements. For a prime \(\ell\neq 7\), the Artin symbol is given by
\[
\operatorname{Frob}_\ell
=
[\ell]\in
(\mathbf Z/7\mathbf Z)^\times/\{\pm1\}.
\]

For \(\ell=2\),
\[
2\not\equiv \pm1\pmod 7.
\]
The class of \(2\) has order \(3\) in
\[
(\mathbf Z/7\mathbf Z)^\times/\{\pm1\}.
\]
Thus
\[
\operatorname{Frob}_2
\]
is a generator of
\[
\operatorname{Gal}(L/\mathbf Q)\cong \mathbf Z/3\mathbf Z.
\]
Hence \(2\) does not split completely in \(L\).

For \(\ell=13\),
\[
13\equiv -1\pmod 7.
\]
Thus the class of \(13\) is trivial in
\[
(\mathbf Z/7\mathbf Z)^\times/\{\pm1\}.
\]
Therefore
\[
\operatorname{Frob}_{13}=1.
\]
Hence \(13\) splits completely in \(L\).

Finally, since \(L/\mathbf Q\) is cyclic, the Hasse norm theorem applies:
\[
a\in N_{L/\mathbf Q}(L^\times)
\iff
a\in N_{L_w/\mathbf Q_v}(L_w^\times)
\quad\text{for all }v.
\]

For a rational prime \(\ell\neq 7\), the local norm condition at \(\ell\) forces the valuation \(v_\ell(\ell)=1\) to be divisible by the residue degree \(f_\ell\). Thus \(\ell\) can be a local norm at \(\ell\) only if
\[
f_\ell=1,
\]
i.e. only if \(\ell\) splits completely in \(L\).

Since \(2\) does not split completely,
\[
\boxed{
2\notin N_{L/\mathbf Q}(L^\times).
}
\]

Since \(13\) splits completely and is locally a norm at every place, the Hasse norm theorem gives
\[
\boxed{
13\in N_{L/\mathbf Q}(L^\times).
}
\]

Thus this example uses global class field theory and Tate cohomology, but not Kummer theory.











\endgroup}
